% Complete documentation on the extended LaTeX mark up used for Python
% documentation is available in ``Documenting Python'', which is part
% of the standard documentation for Python.  It may be found online
% at:
%
%     http://www.python.org/doc/current/doc/doc.html

\documentclass{howto}

%  This is a template for short or medium-size Python-related documents, 
% mostly notably the series of HOWTOs, but it can be used for any
% document you like.   

% The title should be descriptive enough for people to be able to find
% the relevant document. 
%en%\title{GNU Mailman - List Member Manual}
\title{GNU Mailman - リスト会員向けマニュアル}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.03}
% CHANGELOG
% 0.03 Proofreading changes 
% 0.02 Proofreading changes
%   - proofread by Margaret McCarthy and Jason Walton 
% 0.01 First draft of document

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Terri Oda}
\authoraddress{terri(at)zone12.com}

\date{\today}        % XXX update before tagging release!
\release{2.1}        % software release, not documentation
\setreleaseinfo{}    % empty for final release
\setshortversion{2.1}      % major.minor only for software

\begin{document}
\maketitle

% This makes the Abstract go on a separate page in the HTML version;
% if a copyright notice is used, it should go immediately after this.
%
\ifhtml
%en%\chapter*{Front Matter\label{front}}
\chapter*{前付け\label{front}}
\fi

% Copyright statement should go here, if needed.
% ...

% The abstract should be a paragraph or two long, and describe the
% scope of the document.
\begin{abstract}
\noindent
%en%This document describes the list member interface for GNU
%en%Mailman 2.1.  It contains instructions for subscribing, unsubscribing, 
%en%viewing the archives, editing user options, getting password reminders,
%en%and other subscriber-level tasks.  It also answers some common questions
%en%of interest to Mailman list members.
この文書では、GNU Mailman バージョン 2.1 
のリスト会員向けインタフェイスについて説明します。
これには入会、退会、保存書庫の閲覧、会員オプションの変更、
パスワード通知の入手などの、会員レベルの作業が含まれます。
また、Mailman のリスト会員が関心を持つようなよくある質問にも答えます。
\end{abstract}

\tableofcontents

% ===========================================================================
%en%\section{Introduction}
\section{はじめに}

%en%This document is intended to help the members of a Mailman 2.1 mailing list
%en%learn to use the features available to them.  It covers the use of the
%en%web and email interfaces for subscribing and unsubscribing, changing 
%en%member options, getting password reminders and other subscriber-level
%en%tasks.  It also answers some common questions of interest to Mailman list
%en%members.

この文書は、Mailman 2.1 メーリングリストの会員が、
提供されている機能を利用できるようになるための
助けになることをめざしています。
これには入会、退会、保存書庫の閲覧、会員オプションの変更、
パスワード通知の入手などの、会員レベルの作業が含まれます。
また、Mailman のリスト会員が関心を持つようなよくある質問にも答えます。

%en%Information for list and site administrators is provided in
%en%other documents.

リストやサイト全体の管理についての情報は、他の文書を見てください。

%en%This document need not be read in order.  If you are simply looking for
%en%an answer to a specific question, jump to the appropriate place and 
%en%references to other sections will be provided if necessary or potentially 
%en%helpful.

この文書は、順番どおりに読まなくてもかまいません。
あなたが特定の質問の答えを探しているのなら、
適当なところまでとばして、
役に立ちそうな他の節へのリンクをみつけてください。

%en%\note{For the purposes of this document, 
%en%we assume that the reader is familiar with common terms related to email (eg:
%en%Subject line, body of the message) and web sites (eg: drop-down box, button) or
%en%can look them up.  We also assume that the reader can already use his or her
%en%email program and web browser well enough that instructions such as "send email
%en%to this address" or "visit this web page" or "fill in the form provided" are
%en%clear.  If you are not familiar with these actions, you may want to consult
%en%other documentation to learn how to do these things with your particular
%en%setup.} 

\note{この文書を書くにあたって、
筆者はつぎのことを前提にしています。
まず、読者は電子メールに関する一般的な用語
(たとえば、Subject (件名) だとか、メッセージの本文だとか)
や Web に関する用語 (たとえば、テキストボックスだとか、ボタンだとか)
にはなじみがあって、
こういった用語が何を指しているのかわかっているものとします。
また、読者はメールソフトや Web ブラウザを充分うまく使えるようになっていて、
「このアドレスに電子メールを送る」とか「この Web ページへ行く」とか
「フォームに記入する」とかいう指示の意味ははっきり理解できるものとします。
こういった操作になじみがない方は、ほかの参考書などを見て、
自分のコンピュータではどうすればよいのかを学んでおいてください。} 

% ----------------------------------------------------------------------------
%en%\subsection{Acknowledgements}
\subsection{謝辞}

%en%Sections of this document have been borrowed from the List Administrator Manual
%en%found in Mailman CVS, which was written by Barry A. Warsaw, and from the in-line
%en%help for Mailman 2.1.

この文書のいくつかの節は、
Mailman の CVS リポジトリにあった
Barry A. Warsaw 著『the List Administrator Manual』と、Mailman 2.1 の
組込みヘルプメッセージに負っています。

%en%The rest of this manual has been written by Terri Oda.
%en%Terri has been maintaining mailing lists since the year she attained
%en%voting age in Canada, although the two are not related.  She currently
%en%oversees the mailing lists at Linuxchix.org, as well as several smaller
%en%servers.  In the world outside of list administration, Terri is doing
%en%work with an artificial life spam detector, and is actually more of a
%en%programmer than technical writer.

このマニュアルのその他の部分は、Terri Oda が書きました。
Terri は彼女が Canada で参政権を得た年から
メーリングリストの面倒を見てきました
(この 2 つのことは関係ないですが)。
彼女は現在は、Linuxchix.org や
それより小規模な若干のサイトのメーリングリストを管理しています。
In the world outside of list administration, Terri is doing
work with an artificial life spam detector, and is actually more of a
programmer than technical writer.

%en%Proofreading thanks go to Margaret McCarthy and Jason Walton.

原文の校閲は、Margaret McCarthy と Jason Walton がやってくれました。

%WRITEME: More here.  Do we need a license statement here?

日本語への翻訳は、池田 荘児 
\email{nezumi(at)poem.co.jp}
が行ないました。

% ----------------------------------------------------------------------------
%en%\subsection{What is a mailing list?}
\subsection{メーリングリストとは}

%en%A mailing list is simply a list of addresses to which the same information
%en%is being sent.  If you were a magazine publisher, you would have a list of
%en%the mailing addresses of all the subscribers to the magazine.  In the case
%en%of an electronic mailing list, we use a list of email addresses from people
%en%interested in hearing about or discussing a given topic.  

メーリングリストというのは簡単に言うと、
同じ情報が一度に送れるようにするためのアドレスのリストです。
あなたがなにかの会報を発行しているとしたら、
会報の購読者全員の住所のリストを使うでしょう。
電子メールのメーリングリストの場合は、
ある話題について聞きたいとか討議したいとか思っている人たちから
集めた電子メールアドレスのリストを使います。

%en%Two common types of email mailing lists are announcement lists and discussion 
%en%lists.  

代表的な電子メールのメーリングリストには、2 種類あります。
お知らせ用リストと討議用リストです。

%en%Announcement lists are are used so that one person or group can send
%en%announcements to a group of people, much like a magazine publisher's mailing
%en%list is used to send out magazines.  For example, a band may use a mailing list
%en%to let their fan base know about their upcoming concerts.

お知らせ用リストは、個人やグループが多くの人たちにお知らせを送るのに使います。
ちょうど、会報の発行者が住所のリストをつかって会報を発送するようなものです。
たとえば、バンドがメーリングリストをつかって、
ファンに次のコンサートについて知らせるような場合です。

%en%A discussion list is used to allow a group of people to discuss topics amongst
%en%themselves, with everyone able to send mail to the list and have it distributed
%en%to everyone in the group.  This discussion may also be moderated, so only
%en%selected posts are sent on to the group as a whole, or only certain people are
%en%allowed to send to the group.  For example, a group of model plane enthusiasts
%en%might use a mailing list to share tips about model construction and flying.

討議用リストは、多くの人たちが共通の話題について話し合うのに使います。
だれでもリストにメールを送ることができ、
送ったものはみんなに届けられます。
討議を司会付きにして、選ばれた投稿だけが全員に送られるようにしたり、
ごく少数の人たちだけが全員に送れるようにしたりもできます。
たとえば、
模型飛行機マニアのグループでメーリングリストをつかって、
模型の組立てかたや飛ばしかたのこつを教えあうような場合です。

%en%Some common terms:
一般的な用語:
\begin{itemize}
%en%	\item A "post" typically denotes a message sent to a mailing list.  
%en%	(Think of posting a message on a bulletin board.)
	\item 「投稿」とは、
        メーリングリストに送られたメッセージのことを指します。
	(掲示板にメッセージを投稿するようなものです。)
%en%	\item People who are part of an electronic mailing list are usually called 
%en%	the list's "members" or "subscribers."  
	\item 電子メールのメーリングリストに入っている人たちのことは、
        ふつう「会員」とか「参加者」とか言います。
%en%	\item  "List administrators" are the people in charge of maintaining that 
%en%	one list.  Lists may have one or more administrators.
	\item 「リスト管理者」というのは、
        あるひとつのリストの面倒を見る人たちです。
        リストには、それぞれ一人かそれ以上の管理者がいます。
%en%	\item A list may also have people in charge of reading posts and deciding
%en%	if they should be sent on to all subscribers.  These people are called
%en%	list moderators.
	\item リストには、投稿を読んでそれを参加者みんなに送っていいかどうか
        決める係の人たちがいることもあります。
        こういう人たちを「司会者」と言います。
%en%	\item Often more than one electronic mailing list will be run using the same
%en%	piece of software.  The person who maintains the software which runs
%en%	the lists is called the "site administrator."  Often the site administrator
%en%	also administrates individual lists.
	\item 複数のメーリングリストが、
        同じサーバのソフトウェアで動いていることも、よくあります。
        リストを動かすソフトウェアの面倒を見ている人を、
        「サイト管理者」と言います。
        サイト管理者も、なにかのリストの管理者であることが多いです。
\end{itemize}
% ----------------------------------------------------------------------------
\subsection{GNU Mailman}

%en%GNU Mailman is software that lets you manage electronic mailing lists. It
%en%supports a wide range of mailing list types, such as general discussion
%en%lists and announce-only lists.  Mailman has extensive features which make it
%en%good for list subscribers, such as easy subscription and unsubscription, 
%en%privacy options, and the ability to temporarily stop getting posts from the 
%en%list.  The list member features are covered in this document.

GNU Mailman は、
電子メールのメーリングリストを扱えるようにするためのソフトウェアです。
これは、一般的な討議用のリストやお知らせ専用リストなど、
さまざまな種類のメーリングリストに対応しています。
Mailman は、簡単に入会や退会ができたり、
プライバシーを守るための設定ができたり、
一時的にリストから投稿を送るのを停められたりと、
リスト参加者に便利なさまざまな機能を備えています。
この文書では、リスト会員向けの機能を説明しています。

%en%Mailman also has many features which make it attractive to list and site 
%en%administrators.  These features are covered in the list and site administrator
%en%manuals.

Mailman は、リスト管理者やサイト管理者にとっても魅力的な
多くの機能を備えています。こういった機能は、リスト管理者やサイト管理者
向けのマニュアルで説明しています。

% ============================================================================
%en%\section{Translating from our examples to real lists}
\section{例を実際のリストにあてはめる}

%en%Often, it's easier to simply give an example than explain exactly how
%en%to find the address for your specific list.  As such, we'll frequently 
%en%give examples for a fictional list called 
%en%\email{LISTNAME@DOMAIN} whose list information page can be found at
%en%\url{http://WEBSERVER/mailman/listinfo/LISTNAME}.  

それぞれの特定のリストのためのアドレスや URL をどうやって探せばいいかを
きっちり説明するよりも、単に例を示したほうが分かりやすいことが
多いものです。
そういうわけで、この文書ではつぎのような架空のリストの例をよく使います:

\email{LISTNAME@DOMAIN} このリストの案内ページは
\url{http://WEBSERVER/mailman/listinfo/LISTNAME}
になります。

%en%Neither of these are
%en%real addresses, but they show the form of a typical list address.
%en%The capital letters used for the list-specific parts of each address should 
%en%make it easier to see what should be changed for each
%en%list. Although specific list configurations may be different, you will
%en%probably be able to just replace the words given in capital letters with the
%en%appropriate values for a real list:

どちらも、実在のアドレスや URL ではありませんが、
典型的なリストのアドレスや URL の形式になっています。
それぞれのアドレスや URL のうちのリスト固有の部分には大文字を使い、
この部分はリストごとに変わることが分かるようにしています。
リストごとの設定が異なっていても、大文字で書いてある
箇所を実際のリストで使われている名前に置き換えることができるでしょう。

\begin{description}
%en%	\item [LISTNAME] The name of your list.
%en%	\item [DOMAIN] The name of the mail server which handles that list. 
%en%	\item [WEBSERVER] The name of the web server which handles the list web interface.  This may be the same as DOMAIN, and often refers to the same machine, but does not have to be identical. 
%en%\end{description}

	\item [LISTNAME] リストの名前。
        \item [DOMAIN] このリストを運用しているメールサーバのドメイン名。
        \item [WEBSERVER] このリストの Web インタフェイスを運用している
              Web サーバの名前。これは DOMAIN と同じだったり、しばしば
              同じ計算機を指していたりもしますが、一致しなければならない
              わけではありません。
\end{description}

%en%As a real-life example, if you are interested in the mailman-users list, you'd 
%en%make the following substitutions: LISTNAME=mailman-users, DOMAIN=python.org, WEBSERVER=mail.python.org.  As such, for the 
%en%\email{mailman-users@python.org}
%en%mailing list, the list information page can be found at the URL
%en%\url{http://mail.python.org/mailman/listinfo/mailman-users}.  (These, unlike 
%en%most of the examples given in this document, are real addresses.)

実例として、あなたが mailman-users メーリングリストリストに興味があるなら、
つぎのような置き換えができます:
LISTNAME=mailman-users、DOMAIN=python.org、WEBSERVER=mail.python.org。
ですから、
\email{mailman-users@python.org} メーリングリストについては、
リスト案内ページは \url{http://mail.python.org/mailman/listinfo/mailman-users} 
という URL にあります。
(これらのアドレスは、この文書に出てくる大概の例とは違い、
実在のアドレスです。)

%en%Most lists will have this information stored in the \mailheader{List-*} 
%en%headers.  Many
%en%mail programs will hide these by default, so you may have to choose to view
%en%full headers before you can see these informational headers.  

たいていのリストでは、上に挙げたような情報はメッセージの \mailheader{List-*} 
ヘッダに記されます。
多くのメールソフトでは、初期設定ではこのヘッダは隠されますから、
こういった情報ヘッダを見たければすべてのヘッダを表示しておくように
しなければならないかもしれません。

% ============================================================================
%en%\section{Mailman's interfaces}
\section{Mailman のインタフェイス}
%en%Mailman has two different interfaces for the list subscriber: the web 
%en%interface and the email interface.  Most discussion list subscribers use 
%en%the email interface, since this includes the email address you use to send 
%en%mail to all the subscribers of that list.

Mailman には、Web インタフェイスと電子メールインタフェイスという、
2 種類のリスト参加者用インタフェイスがあります。
多くの討議用リストの参加者は、
電子メールインタフェイスを使いますが、
これはそのリストの参加者みんなにメールを送るのに使う電子メールアドレスが
入っているからです。

%en%The interface you use for changing options is largely
%en%a matter of preference, since most (but not all) of the options which can 
%en%be changed from the web interface can also be changed by email.
%en Usually it is easier to use the web interface for 
%en%changing options, since the web interface provides instructions as you go, but
%en%there are times when people may prefer the email interface, so both are 
%en%provided.

オプションを変えるのにどちらのインタフェイスを使うかは、
多分に好みの問題です。
というのは、Web インタフェイスで変えられるオプションのほとんど
(すべてではないですが) は電子メールでも変えられるからです。
ふつうは、オプションを変えるには Web インタフェイスのほうが簡単です。
というのは、Web インタフェイスでは、操作の際に説明が出ますから。
ですが、ときには電子メールインタフェイスのほうを使いたがるひともいるので、
両方のインタフェイスが使えるようになっています。

% ----------------------------------------------------------------------------
%en%\subsection{The web interface\label{sec:web}}
\subsection{Web インタフェイス\label{sec:web}}
%en%The web interface of Mailman is its selling point for many administrators,
%en%since it makes it much easier for subscribers and administrators to see 
%en%which options are available, and what these options do.  
Mailman の Web インタフェイスは、多くの管理者に喜ばれます。
というのは、参加者や管理者がオプションが有効かとか、
そのオプションでなにかできるのかを確かめるのが、
とても簡単になりますから。

%en%Every mailing list is also accessible by a number of web pages.  Note that
%en%the exact URLs are configurable by the site administrator, so they may be
%en%different than what's described below.  We'll describe the most common
%en%configuration, but check with your site administrator or hosting
%en%service for details.

どのメーリングリストも、
さまざまな Web ページでアクセスできるようになっています。
%begin general example
なお、URL そのものはサイト管理者が設定することができるので、
以下で説明するものとは異なるかもしれません。
ここではもっとも一般的な設定について説明しますが、
詳細はあなたのサイトの管理者やホスティングサービス業者に確認してください。
%end general example

\begin{description}
%en%	\item [List information (listinfo) page]
	\item [リスト案内 (listinfo) ページ]
		\begin{itemize}
%en%			\item Usually found at \url{http://WEBSERVER/mailman/listinfo/LISTNAME}
%en%			 (for example, \url{http://lists.example.com/mailman/listinfo/mylist})

			\item ふつうは \url{http://WEBSERVER/mailman/listinfo/LISTNAME} になる
			 (たとえば、 \url{http://lists.example.com/mailman/listinfo/mylist})

%en%			\item The listinfo page is the starting point for the subscriber
%en%			interface.  As one would assume from the name it's given, it 
%en%			contains information about the LISTNAME list.
%en%			Usually all the other subscriber pages can be accessed from this
%en%			point, so you really only need to know this one address.

			\item リスト案内ページは、
                        参加者のインタフェイスの出発点になります。
                        %???
			As one would assume from the name it's given, it 
			contains information about the LISTNAME list.
                        %???
			ふつうは、参加者のためのほかのいろいろなページには
                        ここからアクセスできるので、
                        実際にはこの URL ひとつだけを知っていれば十分です。

		\end{itemize}

%en%	\item [Member options page]
	\item [会員オプションページ]
		\begin{itemize}
%en%			\item Usually found at \url{http://WEBSERVER/mailman/options/LISTNAME/EMAIL}
%en%			(For example, \url{http://lists.example.com/mailman/options/mylist/kathy@here.com})

			\item ふつうは \url{http://WEBSERVER/mailman/options/LISTNAME/EMAIL} になります
			(たとえば、 \url{http://lists.example.com/mailman/options/mylist/kathy@here.com})

%en%			\item This page can also be accessed by going to the listinfo page
%en%			and entering your email address into the box beside the button
%en%			marked "Unsubscribe or Edit Options" (this is near the bottom of the
%en%			page).

			\item リスト案内ページで「退会やオプションの変更」
                        と書いてあるボタン (ページの下のほうにあります) 
                        のそばの
                        テキストボックスに自分の電子メールアドレスを入力して
                        も、このページにアクセスできます。

%en%			\item The member options page allows you to log in/out and change your 
%en%			list settings, as well as unsubscribe or get a copy of your password
%en%			mailed to you. 

			\item 会員オプションページでは、ログインしたり、
                        ログアウトしたり、
                        自分のリスト設定を変えたりできます。また、
                        リストから退会したり、
                        自分のパスワードの控えをメールで送ってもらったりもできます。

%en%			\item \textbf{To log in to your member options page}: 
%en%			If you are not already logged in, there will be a box near the top for
%en%			you to enter your password.  (If you do not know your password, see 
%en%			Section~\ref{sec:getpassword} for more information on getting your 
%en%			password.)  Enter your password in the box and press the button.

			\item \textbf{自分の会員オプションページにログインするには}: 
			まだログインしていなければ、
                        画面の上のほうに自分のパスワードを
                        入力するテキストボックスが出ています。
			(パスワードがわからないときは、
                        \ref{sec:getpassword}~の節 へ行って
                        パスワードを知らせてもらう方法を調べてください。)
			自分のパスワードをテキストボックスに入力し、
                        ボタンを押します。

%en%			\item Once you are logged in, you will be able to view and change
%en%			all your list settings.

			\item ログインがうまくいくと、
                        自分のリスト設定を
                        どれでも見たり変えたりできるようになります。

		\end{itemize}
%en%	\item [List Archives] 
	\item [リストの保存書庫] 
		\begin{itemize}
%en%			\item Usually found at \url{http://WEBSERVER/pipermail/LISTNAME} if the 
%en%			list is publicly archived, and 
%en%			\url{http://WEBSERVER/mailman/private/LISTNAME} if the list is privately
%en%			archives.  (For example, 
%en%			\url{http://lists.example.com/pipermail/mylist} or
%en%			\url{http://lists.example.com/mailman/private/mylist})

			\item ふつうは、リストの保存書庫が公開されているときは
                        \url{http://WEBSERVER/pipermail/LISTNAME} になります。
                        またリストの保存書庫の公開が限定されているときは
			\url{http://WEBSERVER/mailman/private/LISTNAME} 
			になります。 (たとえば、 
			\url{http://lists.example.com/pipermail/mylist} や
			\url{http://lists.example.com/mailman/private/mylist})

%en%			\item The list archive pages have copies of the posts sent to the
%en%			mailing list, usually grouped by month.  In each monthly group, the
%en%			posts are usually indexed by author, date, thread, and subject.

			\item リストの保存書庫のページには、
                        メーリングリストに送られた投稿のコピーがあって、
                        ふつうは月ごとにまとめてあります。
                        月ごとのまとまりごとに、
                        投稿が発信者順、日付順、スレッド順、件名順に並べてあります。

%en%			\item \note{Pipermail is the name of the default archiver that
%en%			comes with Mailman.  Other archive programs are available.}

			\item \note{Pipermail というのは、Mailman に標準で
                        含まれている保存書庫作成プログラムの名前です。
                        ほかの保存書庫プログラムもあります。}

%en%			\item If the archive is private, you will need to supply your
%en%			subscribed email address and your password to log in.  (See
%en%			Section~\ref{sec:getpassword} for more information on getting
%en%			your password.)
			\item 保存書庫の公開が限定されているときは、
                        自分の登録電子メールアドレスと自分のパスワードを
                        入れてログインしなければなりません。
			(パスワードがわからなくなったときは
                        \ref{sec:getpassword}~の節 を見てください。)
		\end{itemize}
\end{description}

% ----------------------------------------------------------------------------E
%en%\subsection{The email interface\label{sec:email}}
\subsection{電子メールインタフェイス\label{sec:email}}
%en%Every mailing list has a set of email addresses to which messages can be 
%en%sent.  There's always one address for posting messages to the list, one
%en%address to which bounces are sent, and addresses for processing email
%en%commands.  For a fictional mailing list called
%en%\email{mylist@example.com}, you'd find these addresses:

どのメーリングリストにも、電子メールアドレスが
ひとそろいあって、そこへメッセージを送れます。
メッセージを投稿するためのアドレスがひとつ、
配送エラーを受け付けるアドレスがひとつ、そして電子メールコマンドを処理する
アドレスがいくつかあります。ある架空のメーリングリスト
\email{mylist@example.com} だと、つぎのようなアドレスがあります:

\begin{itemize}
%en%\item \email{mylist@example.com} -- this is the email address people should
%en%      use for new postings to the list.

\item \email{mylist@example.com} -- これは、
リストに新たな投稿をするのに使うアドレスです。

%en%\item \email{mylist-join@example.com} -- by sending a message to this address,
%en%      a new member can request subscription to the list.  Both the
%en%      \mailheader{Subject} header and body of such a message are
%en%      ignored.  Note that mylist-subscribe@example.com is an alias for
%en%      the -join address.

\item \email{mylist-join@example.com} -- このアドレスにメッセージを送ることで、
      リストに入会の申請ができます。このとき、メッセージの
      \mailheader{Subject} ヘッダ (件名) も本文も無視され、
      誰にも読まれません。
      なお、mylist-subscribe@example.com は
      この -join アドレスとおなじはたらきをします。

%en%\item \email{mylist-leave@example.com} -- by sending a message to this address,
%en%      a member can request unsubscription from the list.  As with the
%en%      -join address, the \mailheader{Subject} header and body of the
%en%      message is ignored.  Note that mylist-unsubscribe@example.com is
%en%      an alias for the -leave address.

\item \email{mylist-leave@example.com} -- このアドレスにメッセージを送ることで、
      リストに退会の申請ができます。-join アドレスと同じく、メッセージの
      \mailheader{Subject} ヘッダ (件名) も本文も無視され、
      誰にも読まれません。
      なお、mylist-unsubscribe@example.com は
      この -leave アドレスとおなじはたらきをします。

%en%\item \email{mylist-owner@example.com} -- This address reaches the list owner
%en%      and list moderators directly.  This is the address you use if 
%en%		you need to contact the person or people in charge.

\item \email{mylist-owner@example.com} -- このアドレスに送ったものは、
      リストの管理者と司会者に直接届きます。
      このアドレスは、リスト運営に関わる人間 (システムではなく) 
      に連絡をとりたいときに使います。

%en%\item \email{mylist-request@example.com} -- This address reaches a mail robot
%en%      which processes email commands that can be used to set member
%en%      subscription options, as well as process other commands.
%en%      A list of members' email commands is provided in 
%en%		Appendix~\ref{a:commands}.

\item \email{mylist-request@example.com} -- このアドレスに送ったものは、
      電子メールコマンドを処理するプログラムに届きます。
      会員の登録オプションの設定などのコマンドを処理できます。
      リスト会員用の電子メールコマンドの説明は付録~\ref{a:commands}
      にあります。

%en%\item \email{mylist-bounces@example.com} -- This address receives bounces from
%en%      members whose addresses have become either temporarily or
%en%      permanently inactive.  The -bounces address is also a mail robot
%en%      that processes bounces and automatically disables or removes
%en%      members as configured in the bounce processing settings.  Any
%en%      bounce messages that are either unrecognized, or do not seem to
%en%      contain member addresses, are forwarded to the list
%en%      administrators.

\item \email{mylist-bounces@example.com} -- このアドレスは、
      一時的あるいは恒久的につかえなくなっているアドレスの
      会員からの配送エラーを受け取ります。
      -bounces アドレスの送り先はプログラムで、
      リストの配送エラー処理設定にしたがって
      配送エラーを処理し、自動的にその会員への
      配送を停めたり、登録を解除したりします。
      メッセージに含まれている配送エラーの内容を検知できなかったり、
      会員のアドレスが含まれているかどうか判定できなかった場合は、
      メッセージはリスト管理者に回送されます。

%en%\item \email{mylist-confirm@example.com} -- This address is another email
%en%      robot, which processes confirmation messages for subscription
%en%      and unsubscription requests.
\item \email{mylist-confirm@example.com} -- このアドレスもプログラムに行きます。
      これは入会や退会の申請に対する確認メッセージを処理します。
\end{itemize}

%en%There's also an -admin address which also reaches the list administrators,
%en%but this address only exists for compatibility with older versions of
%en%Mailman.

ほかに、-admin アドレスもあります。
このアドレス宛てのものはリスト管理者に届きますが、
古いバージョンの Mailman との互換性のためにあるだけなので、
使わないほうがいいでしょう。

%en%For changing options, we use the \email{LISTNAME-request}
%en%address (for example, \email{mylist-request@example.com}).

オプションを変えるには、\email{LISTNAME-request}
アドレスを使います (たとえば、 \email{mylist-request@example.com})。

%en%Commands can appear in the subject line or the body of the message.  Each 
%en%command should be on a separate line.  If your mail program automatically
%en%appends a signature to your messages, you may want to put the word
%en%"\var{end}" (without the quotes) on a separate line after your other commands. 
%en%The \var{end} command tells Mailman not to process the email after that
%en%point.

コマンドは、メッセージの subject (件名) にも、本文にも書けます。
コマンドごとに改行を入れなければなりません。
あなたのメールソフトがメッセージの最後に自動的に署名を付け加えるように
なっている場合は、
「\var{end}」(鍵括弧は書かない) を、
コマンドの最後の行のつぎの行に書くとよいでしょう。
\var{end} コマンドがあると、Mailman は電子メールのそれよりあとに書いて
あるものを処理しません。

%en%The most important command is probably the "\var{help}" command, since it 
%en%makes Mailman return a message full of useful information about the
%en%email commands and directions to the web interface.

最重要コマンドはおそらく「\var{help}」コマンドでしょう。というのは
このコマンドに対して Mailman は電子メールコマンドについての有用な情報と、
Web インタフェイスについての説明を送り返すからです。

%en%Quick references to the subscriber commands have been provided in 
%en%Appendices \ref{a:commands} and \ref{a:options}. (These have been slightly
%en%adapted from the output of the \var{help} command.)

参加者用コマンドのクイックリファレンスが、
付録の \ref{a:commands} と \ref{a:options} にあります。
(これは \var{help} コマンドの出力に若干変更を加えたものです。)

% ============================================================================
%en%\section{I need to talk to a human!\label{sec:human}}
\section{人間と話したいんですが...\label{sec:human}}

%en%If you have any trouble with any of these commands, you can always reach the
%en%person or people in charge of a list by using the list administrator email address. 
%en%The list administrators can help you figure out
%en%how to do something, subscribe/unsubscribe you, or change your 
%en%settings if you are unable to change them yourself for some reason.  Please
%en%remember that many mailing list administrators are volunteers who are donating
%en%their spare time to run the list, and they may be very busy people.

リストを利用するうえでなにか困ったことがあったら、
リスト管理者の電子メールアドレスを使って、
リストのめんどうを見ている人 (たち) にいつでも連絡することができます。
リスト管理者は、あなたがどうしたらいいのか教えてくれたり、
あなたを入会させたり退会させたり、
あなたがなんらかの理由で自分で設定を変えられないときに変えてくれたりする
かもしれません。
ただし、忘れないでいただきたいのですが、多くのリスト管理者が
ボランティアで、自分の時間を割いてリストの運営をしているのです。
なかにはとても忙しくて、すぐには返事ができない人もいるかもしれません。

%en%This list administrator email address is in the form \email{LISTNAME-owner@DOMAIN}, where LISTNAME is the name of the list (eg: mailman-users) and DOMAIN is
%en%the name of the server (eg: python.org).  
%en%This email address, 
%en%along with the email addresses of specific administrators, is given on the 
%en%bottom of the list information pages. See Section~\ref{sec:web} for more 
%en%information on finding the list information page for your list

そのリスト管理者の電子メールアドレスですが、
\email{LISTNAME-owner@DOMAIN} となります。
ここで LISTNAME はリストの名前 (たとえば mailman-users) で、
%begin general example
DOMAIN はサーバのドメイン名 (たとえば python.org) です。 
%end general example
この電子メールアドレスは、個々の管理者の電子メールアドレスとともに、
リスト案内ページの下部に表示されています。
自分のリストのリスト案内ページを見付けるには詳しくは \ref{sec:web}~節
を見てください。

% ============================================================================
%en%\section{Subscribing and unsubscribing}
\section{入会と退会}
%en%Since subscribing (joining) and unsubscribing (leaving) lists are often the 
%en%only things a list member needs to know, these can both be done without 
%en%requiring you to know a password.
リスト参加者は、
入会 (参加) と退会 (脱退) さえ知っていれば用が足りることも多いです。
そのため、どちらも自分のパスワードが分からなくてもできるようになっています。

% ----------------------------------------------------------------------------
%en%\subsection{How do I join a list? (subscribe)\label{sec:subscribe}}
\subsection{リストに入るには (入会)\label{sec:subscribe}}

%en%There are two common ways you can subscribe to a Mailman mailing list. 
Mailman のメーリングリストに入会するには、主に 2 つの方法があります。

%en%Using the web interface:
Web インタフェイスでは:
\begin{enumerate}
%en%	\item Go to the list information page for the list you want to join. 
%en%	(This will probably be something like 
%en%	\url{http://WEBSERVER/mailman/listinfo/LISTNAME})
%en%	\item Look for the section marked "Subscribing to LISTNAME" and fill in the 
%en%	boxes.  You can fill in the following:
	\item 入りたいリストのリスト案内ページへ行きます。
	(これはたぶん
	\url{http://WEBSERVER/mailman/listinfo/LISTNAME}
        といった場所でしょう)
	\item 「LISTNAME の購読」と見出しのあるセクションを探して、
        テキストボックスに記入します。つぎのような記入欄があります:
	\begin{itemize}
%en%		\item You \emph{must} enter your email address.
%en%		\item You may choose to supply your real name.
%en%		\item You may choose a password.   If you do not choose one, Mailman will
%en%		 generate one for you.  
		\item あなたの電子メールアドレスを\emph{必ず}入力します。
		\item あなたの名前を入れることもできます。
		\item パスワードを決めることができます。
                 決めなかったときは、Mailman が自動的に決めます。

%en%		\warning{Do NOT use a valuable password, since this 
%en%		password may be mailed to you in plain text.  }
%en%		\item If the list supports more than one language, you may be able to 
%en%		choose your preferred language.  \note{This setting does not affect
%en%		posts to the list, only pre-prepared Mailman texts such as your member
%en%		options page.}

		\warning{大事なパスワードを使わないようにしてください。
                ここで入力したパスワードは平文のまま、
		あなたにメールで送られます。}
		\item リストが複数の言語に対応しているなら、
                使う言語を選ぶこともできます。
		\note{この設定はリストへの投稿には影響しません。
		あなたの会員オプションページのように、
                あらかじめ用意されている Mailman の文章が変わるだけです。}
	\end{itemize}
%en%	\item Press the subscribe button.  A new page should appear telling you 
%en%	that your request has been sent.
	\item [入会を申し込む] ボタンを押します。
        ページが変わって、申請が送られたという表示になるはずです。
\end{enumerate}

%en%Using the email interface:
電子メールインタフェイスでは:
\begin{enumerate}
%en%	\item Open a mail program which sends mail from the address you want to
%en%	subscribe.
%en%	\item Send a mail to the list subscription address, which will be in the 
%en%	form \email{LISTNAME-join@DOMAIN}.  The subject and body
%en%	of the message will be ignored, so it doesn't matter what you put there.
	\item メールソフトを起動して、あなたが登録したいと思うアドレスから
        メールを送れるようにします。
	\item リストの入会アドレスにメールを送ります。
	これは \email{LISTNAME-join@DOMAIN} というアドレスになります。
	メッセージの subject (件名) や本文は無視され、誰にも読まれません。
	ですから何か書いてあってもかまいませんし、書いてなくてもかまいません。
\end{enumerate}

%en%After following one of these sets of instructions (you don't need to do
%en%both!), there are a few possible outcomes depending upon the settings for
%en%that list. 
上の手順のどちらかひとつ (両方やる必要はありません) をしたあと
どういうことが起こるかは、それぞれのリストの設定によって違います。
\begin{itemize}
%en%	\item You may receive an email message asking for confirmation that you 
%en%really want to be subscribed to the list.  This is to prevent anyone from
%en%subscribing you to lists without your permission.  Follow the instructions
%en%given in the message to confirm your wish to be subscribed.
%en%	\item A moderator may also need
%en%to confirm your subscription if you are subscribing to a limited list.  
%en%	\item Or
%en%you may have to wait for a moderator \textit{and} follow the instructions in
%en%the confirmation mail.
	\item あなたが本当に入会したいのかどうか確認を求める
	電子メールが届くかもしれません。
	これは誰かがあなたの許可なくあなたを登録してしまうのを防ぐためです。
	そのメッセージに書いてある手順にしたがって、あなたに入会の意思がある
	ことを確認します。
	\item 限定リストへの入会だった場合、
	司会者の承認が要ります。
	\item 司会者の承認を待って、\textit{さらに} 確認メールの
        手順にしたがって確認しなければならないかもしれません。
\end{itemize}

%en%Once this is done, you will likely receive another message welcoming you to
%en%the list.  This message contains some useful information including your list
%en%password and some quick links for changing your options, so you may want to
%en%save it for later reference.

このような手順が終ると、さらにリストへの入会を歓迎するメッセージが届くことが
あります。このメッセージには、あなたのリスト会員パスワードや、
あなたの会員オプションを変えるための URL へのリンクなど、
大事な情報が書いてあるので、
保存してあとで見られるようにしておくとよいでしょう。

%en%\note{Subscribing can be done in other ways as well.  See 
%en%Appendix~\ref{a:commands} for more advanced email subscribing commands.}

\note{入会はほかのやりかたでもできます。
電子メールでの高度な入会コマンドについては、付録~\ref{a:commands} 
を見てください。}

% ----------------------------------------------------------------------------
%en%\subsection{How do I leave a list? (unsubscribe)\label{sec:unsubscribe}}
\subsection{リストから抜けるには (退会)\label{sec:unsubscribe}}

%en%Don't want to be on a list any more?  If you're just going on vacation or
%en%are too busy to read mails and want to temporarily turn them off, you may want
%en%to stop mail delivery rather than unsubscribing.  This means you keep your
%en%password and other settings so you can, for example, still have access to 
%en%private list archives.  If this is what you'd
%en%prefer, see Section~\ref{sec:nomail} for instructions on disabling mail
%en%delivery temporarily.

もうリストに戻ってくることはないのでしょうか。
休暇に入るとか、忙しくてメールを読む暇がないのでしばらく停めたいだけなら、
退会しなくても配送だけ停めておくこともできます。つまり、
あなたのパスワードや設定などはそのまま残しておくことができるので、
公開限定の保存書庫にアクセスしたりするようなことはできます。
このようにしたほうがよければ、
\ref{sec:nomail}~節で、
一時的にメール配送を停止するための手順を見てください。

%en%If you actually want to leave the list, there are two common ways you can
%en%unsubscribe from a Mailman mailing list.

本当にリストから抜けたいのなら、
Mailman のメーリングリストから退会する方法は主に 2 つあります。

%en%Using the web interface:
Web インタフェイスでは:
\begin{enumerate}
%en%	\item Go to the list information page for the list you want to leave.
%en%	(This will probably be something like 
%en%	\url{http://WEBSERVER/mailman/listinfo/LISTNAME})
%en%	\item Look for the section marked "LISTNAME subscribers" (usually found 
%en%	near the bottom of the page).
%en%	\item There should be a button marked "Unsubscribe or Edit Options."  
%en%	Enter your email address in the box beside this button and press the
%en%	button.
%en%	\item You should be brought to a new page which has an "Unsubscribe"
%en%	button.  Press it to unsubscribe and follow the instructions given.
	\item 抜けたいリストのリスト案内ページへ行きます。
	(これはたぶん
	\url{http://WEBSERVER/mailman/listinfo/LISTNAME}
        といった場所でしょう)
	\item 「LISTNAME 会員の方へ」と見出しのあるセクションを探します
        (ふつうはページの下のほうにあります)。
	\item 「退会またはオプションの変更」と書いてあるボタンがあります。
	ボタンのそばのテキストボックスにあなたの電子メールアドレスを
        入力し、ボタンを押します。
	\item 「退会」ボタンがあるページに変わります。
	退会するならそのボタンを押して、表示される手順にしたがいます。
\end{enumerate}

%en%Using the email interface:
電子メールインタフェイスでは:
\begin{enumerate}
%en%	\item Open a mail program which sends mail from the address you want to 
%en%	unsubscribe.
%en%	\item Send a mail to the list unsubscribe address, which will be of the form
%en%	\email{LISTNAME-leave@DOMAIN}.  
%en%	The subject and body
%en%	of this message will be ignored, so it doesn't matter what you put there.
	\item メールソフトを起動して、あなたが退会させたいと思うアドレスから
        メールを送れるようにします。
	\item リストの退会アドレスにメールを送ります。
	これは \email{LISTNAME-leave@DOMAIN} というアドレスになります。
	メッセージの subject (件名) や本文は無視され、誰にも読まれません。
	ですから何か書いてあってもかまいませんし、書いてなくてもかまいません。
\end{enumerate}

%en%After following one of these sets of instructions (you don't need to do
%en%both!), you will be sent a confirmation mail and must follow the
%en%instructions given in that mail to complete the unsubscription.  This is to
%en%stop people from unsubscribing you without your permission.  In addition, a
%en%moderator may need to approve your unsubscription.

上の手順のどちらかひとつ (両方やる必要はありません) をしたあと、
あなたには確認メールが届きます。
このメールに書いてある手順にしたがわなければ退会が完了しません。
これは、誰かがあなたの許可なくあなたを退会させてしまうのを防ぐためです。
この手順に加え、
司会者があなたの退会を承認しなければいけないときもあります。

%en%If you do not receive this confirmation mail with instructions, make sure
%en%that you typed your email address correctly (if you were using the web 
%en%interface to unsubscribe) and that the address you tried
%en%to unsubscribe is, indeed, actually subscribed to that list.  For security
%en%reasons, Mailman generates the same member options page regardless of
%en%whether the address entered is subscribed or not.  This means that people
%en%cannot use this part of the web interface to find out if someone is
%en%subscribed to the list, but it also means that it's hard to tell if you just
%en%made a typo.

手順の書いてある確認メールが届かないようなら、
あなたの電子メールアドレスを打ち間違えていないか (退会にWeb インタフェイスを
使っている場合)、退会させようとしているアドレスが実際にリストに登録されて
いるものと同じがどうか、を確かめます。
安全確保上の理由から、Mailman は、
入力されたアドレスが登録されているかどうかに関わらず、
まったく同じ内容の会員オプションページを表示します。ですから、
Web インタフェイスのこの部分を使ってだれがリストに入会しているかを
調べることはできませんが、
アドレスを打ち間違えていても教えてはくれないというわけです。

%en%Once your unsubscription has been processed, you will will probably receive
%en%another message confirming your unsubscription from the list, and at that
%en%point you should stop receiving messages.

退会が処理されると、
さらにリストからの退会を知らせるメッセージが届くこともあります。
いずれにせよ、このときから、あなたにはメッセージが送られてこなくなります。

%en%If you wish to skip the confirmation process (for example, you might be
%en%unsubscribing an address which no longer works), it is possible to bypass it by
%en%using your password instead and either logging in to your options page using
%en%it (See Section~\ref{sec:web}), or sending it with your email commands to
%en%LISTNAME-request (See Appendix~\ref{a:commands} for advanced email 
%en%unsubscription commands). See Section~\ref{sec:getpassword} for more 
%en%information on getting your password.

確認の処理をとばしたい (たとえば、あなたのアドレスがもう使えなくなったので
退会させたい、など) ときは、かわりにあなたの会員パスワードを使って
オプションページにログインする (\ref{sec:web}~節を見てください) か、
LISTNAME-request アドレスに電子メールコマンドを送る
(電子メールでの高度な退会コマンドについては、
付録~\ref{a:commands} を見てください)
かすることで、確認を省略できます。
パスワードが分からなくなったときは、
\ref{sec:getpassword}~節を見てください。

% ============================================================================
%en%\section{Passwords\label{sec:password}}
\section{会員パスワード\label{sec:password}}
%en%Your password was either set by you or generated by Mailman when you
%en%subscribed. 
%en%You probably got a copy of it in a
%en%welcome message sent when you joined the list, and you may also receive a
%en%reminder of it every month.  It is used to verify your identity to Mailman
%en%so that only the holder of the password (you!) and the administrators
%en%can view and change your settings.  

あなたの会員パスワードは、入会したときに、あなたが決めたか
Mailman によって自動的に決められたかのどちらかです。
パスワードの控えは、リストに参加したときに送られてきた
「ようこそ」メッセージに書いてあったはずです。
また、パスワード通知を毎月おくってもらうようにもできます。
Mailman はこのパスワードを使ってあなたを認証するので、
会員パスワードの持ち主 (あなたのことです) とリスト管理者以外は、
あなたの設定を見たり変えたりすることはできません。

%en%\warning{Do NOT use a valuable password for Mailman, since it can be
%en%sent in plain text to you.}

\warning{大事なパスワードを Mailman 用に使わないでください。
 このパスワードは平文のまま、あなたにメールで送られます。}

% ----------------------------------------------------------------------------
%en%\subsection{How do I get my password?\label{sec:getpassword}}
\subsection{自分のパスワードを知りたい\label{sec:getpassword}}
%en%If you've forgotten your password and haven't saved the welcome message or 
%en%any reminder messages, you can always get a reminder through the web interface:
自分の会員パスワードを忘れてしまい、
「ようこそ」メッセージやパスワード通知も保存していなかったとしても、
Web インタフェイスを使っていつでもパスワード通知を取り寄せることができます:

\begin{enumerate}
%en%	\item Go to the list information page for the list from which you wish to 
%en%	get your password
%en%	(This will probably be something like 
%en%	\url{http://WEBSERVER/mailman/listinfo/LISTNAME})
%en%	\item Look for the section marked "LISTNAME subscribers" 
%en%	(this section is usually found near the bottom of the page).
%en%	\item There should be a button marked "Unsubscribe or Edit Options."  
%en%	Enter your email address in the box beside this button and press the
%en%	button.
%en%	\item You should be brought to a new page which has an "Password 
%en%	Reminder" section.  Press the "Remind" button to have your password
%en%	emailed to you.
	\item パスワードを知りたいリストのリスト案内ページへ行きます
	(これはたぶん
	\url{http://WEBSERVER/mailman/listinfo/LISTNAME}
        といった場所でしょう)
	\item 「LISTNAME 会員の方へ」と見出しのあるセクションを探します
        (ふつうはページの下のほうにあります)。
	\item 「退会またはオプションの変更」と書いてあるボタンがあります。
	ボタンのそばのテキストボックスにあなたの電子メールアドレスを
        入力し、ボタンを押します。
	\item 「パスワード通知」というセクションのあるページに変わります。
	「通知」ボタンを押すと、
	会員パスワードが電子メールであなたに送られます。
\end{enumerate}

%en%If you do not receive the password reminder email after doing this, make sure 
%en%that you typed your
%en%email address correctly and that the address you used is, indeed, actually
%en%subscribed to that list.  For security reasons, Mailman generates the same
%en%member options page regardless of whether the address entered is subscribed
%en%or not.  This means that people cannot use this part of the web interface to
%en%find out if someone is subscribed to the list, but it also means that it's
%en%hard to tell if you just made a typo.

これをしてもパスワード通知の電子メールが送られてこないようなら、
正しい電子メールアドレスをタイプしたのか、またそのアドレスは
たしかにそのリストに登録しているものなのかどうか、を確かめてください。
安全確保上の理由から、Mailman は、
入力されたアドレスが登録されているかどうかに関わらず、
まったく同じ内容の会員オプションページを表示します。ですから、
Web インタフェイスのこの部分を使ってだれがリストに入会しているかを
調べることはできませんが、
アドレスを打ち間違えていても教えてはくれないというわけです。

電子メールインタフェイスを使っても、パスワード通知を取り寄せることができます:
\begin{enumerate}
	%en%\item Send a mail to \email{LISTNAME-request@DOMAIN} with the command 
	%en%\var{password}
	\item \email{LISTNAME-request@DOMAIN} に、\var{password} コマンドを
	書いた電子メールを送ります。

	%en%Commands can appear
	%en%in either the body or the subject of the message.  (See 
	%en%Section~\ref{sec:email} for more information about sending mail
	%en%commands.)  

	コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
	(メールコマンドの送りかたについて詳しくは、
	\ref{sec:email}~節を見てください。)

	%en%If you are not sending mail from your subscribed address, you can also
	%en%specify this address by sending the command \nolinebreak{\var{password~address=<ADDRESS>}}.

	リストに登録していないアドレスからメールを送るのなら、
	\nolinebreak{\var{password~address=アドレス}} 
	というコマンドを書いて、
	登録アドレスを指定することもできます。
\end{enumerate}

% ----------------------------------------------------------------------------
%en%\subsection{How do I change my password?}
\subsection{自分のパスワードを変えるには}
%en%		\warning{Do NOT use a valuable password, since this 
%en%		password may be mailed to you in plain text.  }
		\warning{大事なパスワードを使わないでください。
		このパスワードは平文のまま、あなたにメールで送られます。}

%en%From the web interface:
Web インタフェイスでは:
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} for 
%en%   instructions on how to do this.)
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)

%en%	\item Look for the password changing boxes on the right-hand side of the
%en%	page and enter your new password in the appropriate boxes, then press the
%en%	button marked "Change My Password."
	\item ページの右側の、パスワード変更のテキストボックスを探します。
	そして、それぞれのテキストボックスにあなたの新しいパスワードを
	入力し、「パスワード変更」というボタンを押します。
\end{enumerate}

%en%This can also be changed for multiple lists at the same time if you are subscribed to 
%en%more than one list on the same domain.  See Section~\ref{sec:global} for 
%en%information about changing settings globally.

おなじドメインの複数のリストに登録しているのなら、
一度にすべてのリストのパスワードを変えることもできます。
「全部変更」について詳しくは、\ref{sec:global}~節を見てください。

%en%From the email interface:
電子メールインタフェイスでは:
\begin{enumerate}
%en%	\item Send a mail to \email{LISTNAME-request@DOMAIN} with the command 
%en%	\nolinebreak{\var{password~<OLDPASSWORD>~<NEWPASSWORD>}}.  

	\item \email{LISTNAME-request@DOMAIN} に、
	\nolinebreak{\var{password~元のパスワード~新しいパスワード}}
	というコマンドを書いた電子メールを送ります。

%en%	Commands can appear
%en%	in either the body or the subject of the message.  (See 
%en%	Section~\ref{sec:email} for more information about sending mail
%en%	commands.)  

	コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
	(メールコマンドの送りかたについて詳しくは、
	\ref{sec:email}~節を見てください。)

%en%	If you are not sending mail from your membership address, you can also
%en%	specify this address with \var{address=<ADDRESS>} after <NEWPASSWORD>.
	
	リストに登録していないアドレスからメールを送るのなら、
	新しいパスワード の後に \var{address=アドレス}
	を書いて、
	登録アドレスを指定することもできます。

%en%	For example, if \email{kathy@here.com} wanted to change her \var{mylist}
%en%	password from \var{zirc} to \var{miko}, but she was sending mail from 
%en%	her work address \email{kathy@work.com}, she could send a message
%en%	to \email{mylist-request@example.com} with the subject set to 
%en%	\nolinebreak{\var{password~zirc~miko~address=kathy@here.com}}.

	たとえば、\email{kathy@here.com} が \var{mylist}
	メーリングリストでの自分の会員パスワードを
	\var{zirc} から \var{miko} に変えたいが、メールを職場のアドレス
	\email{kathy@work.com} から送っているときは、
	彼女は \email{mylist-request@example.com} に、件名を
	\nolinebreak{\var{password~zirc~miko~address=kathy@here.com}}
	としたメッセージを送ればよいわけです。
\end{enumerate}

% ----------------------------------------------------------------------------
%en%\subsection{How do I turn password reminders on or off? (reminders option)}
\subsection{パスワード通知 を 送ってもらう
ようにしたり、停めたりするには (パスワード通知オプション)}
%en%If you don't wish to the reminder email including your password every month, 
%en%you can disable it from the member options page.  (You can always get the
%en%password mailed out when you actually want it.  See 
%en%Section~\ref{sec:getpassword} for instructions.)
パスワード通知の電子メールを毎月送ってほしくないのであれば、
会員オプションページで停めることができます。
(パスワードをすぐに知りたければ、いつでもメールで取り寄せることができます。
手順は \ref{sec:getpassword}~節を見てください。)

%en%Using the web interface:
Web インタフェイスでは:
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} for 
%en%	instructions on how to do this.)
%en%	\item Look for the section marked "Get password reminder email for this
%en%	list?" and change the value accordingly.\
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「このリストについてパスワード通知を受け取りますか?」
	というセクションを探し、設定を好きなように変えます。
\end{enumerate}

%en%This can also be changed for multiple lists at the same time if you are subscribed to 
%en%more than one list on the same domain.  See Section~\ref{sec:global} for 
%en%information about changing settings globally.

おなじドメインの複数のリストに登録しているのなら、
一度にすべてのリストの設定を変えることもできます。
「全部変更」について詳しくは、\ref{sec:global}~節を見てください。

%en%Using the email interface:
電子メールインタフェイスでは:
\begin{enumerate}
%en%   \item Send a mail to \email{LISTNAME-request@DOMAIN} with the command
%en%   \var{set~reminders~on} or \var{set~reminders~off}.
   \item \email{LISTNAME-request@DOMAIN} に、
   \var{set~reminders~on} あるいは \var{set~reminders~off}
   というコマンドを書いた電子メールを送ります。

%en%   Commands can appear
%en%   in either the body or the subject of the message.  (See
%en%   Section~\ref{sec:email} for more information about sending mail
%en%   commands.)
   コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
   (メールコマンドの送りかたについて詳しくは、
   \ref{sec:email}~節を見てください。)

%en%	\item Set it to "on" to receive reminders, and "off" to stop receiving
%en%	reminders.
	\item 「on」にすると通知が送られるようになります。
	「off」にすると通知が送られないようになります。
\end{enumerate}


% ============================================================================
%en%\section{Changing mail delivery}
\section{メールの配送のしかたを変える}
% ----------------------------------------------------------------------------
%en%\subsection{How do I turn mail delivery on or off? 
%en%	(delivery option)\label{sec:nomail}}
\subsection{メール配送 を 停止したり、再開
したりするには (メール配送オプション)\label{sec:nomail}}

%en%You may wish to temporarily stop getting messages from the 
%en%list without having to unsubscribe.
%en%If you disable mail delivery, you will no longer receive messages, but will
%en%still be a subscriber and will retain your password and other settings.  

退会したくはないけれど、
リストからメッセージを送ってもらうのを
一時的に停めたいこともあるかもしれません。
メール配送を停止すれば、メッセージは送られてこなくなりますが、
参加者のままでいられるので、
あなたのパスワードなどの設定は残しておけます。

%en%This can be handy in a many different cases.  For example, you could be 
%en%going on vacation or need a break from the list because you're too busy to 
%en%read any extra mail. 
%en%Many mailing lists also allow only subscribers to post to the list, so if you
%en%commonly send mail from more than one address (eg, one address for at home
%en%and another for when you're travelling), you may want to have more than
%en%one subscribed account, but have only one of them actually receive mail.
%en%You can also use this as a way to read private archives even on a list which
%en%may be too busy for you to have sent directly to your mailbox.  All you need to do is subscribe, disable mail delivery, and use your password and email to 
%en%log in to the archives.

これはいろいろな場合に便利なことがあります。
たとえば、あなたが休暇に入ったり、
とても忙しくなって余計なメールを読む暇がなくなったりして、
しばらくリストを離れなければならないときです。
またたとえば、
投稿を参加者からのものに限るようになっているリストは多いですが、
あなたが主に複数のアドレスからメールを送っている
(たとえば自宅のアドレスのほかに旅行中のアドレスもある) のなら、
複数のアドレスで入会しておいて、
そのうちのひとつだけでメールを受け取るようにしておきたいでしょう。
あるいはたとえば、リストの投稿量がたいへん多くて、
メールで受け取っていたのでは
あなたのメールボックスがあふれてしまいそうなときに、
リストから抜けずに公開限定の保存書庫で読む、といったことにも使えます。
まず入会し、メール配送を停止し、
自分のパスワードと電子メールアドレスで保存書庫にログインすればいいのです。

%en%To disable/enable mail delivery using the web interface:
Web インタフェイスで配送を停止したり有効にしたりするには:
\begin{enumerate}
%en%	\item Log in to your options page. (See Section~\ref{sec:web} for instructions.)
%en%	\item Go down to the section marked "Mail delivery" and select "Disabled"
%en%		to stop receiving mail, and "Enabled" to start receiving mail.
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「メール配送」
	というセクションを探し、メールを送ってもらうのを停めるときは
	「停止」、送ってもらうときは「有効」を選びます。
\end{enumerate}

%en%This can also be changed for multiple lists at the same time if you are subscribed to 
%en%more than one list on the same domain.  See Section~\ref{sec:global} for 
%en%information about changing settings globally.

おなじドメインの複数のリストに登録しているのなら、
一度にすべてのリストの設定を変えることもできます。
「全部変更」について詳しくは、\ref{sec:global}~節を見てください。

%en%To disable/enable mail delivery using the email interface:
電子メールインタフェイスで配送を停止したり有効にしたりするには:
\begin{enumerate}
%en%   \item Send a mail to \email{LISTNAME-request@DOMAIN} with the command
%en%   \var{set~delivery~off} or \var{set~delivery~on}.
   \item \email{LISTNAME-request@DOMAIN} に
   \var{set~delivery~off} または \var{set~delivery~on} 
   というコマンドを書いたメールを送ります。

%en%   Commands can appear
%en%   in either the body or the subject of the message.  (See
%en%   Section~\ref{sec:email} for more information about sending mail
%en%   commands.) 
%en%	\item Set it to "off" to stop receiving posts, and "on" to start
%en%	receiving them again.
   コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
   (メールコマンドの送りかたについて詳しくは、
   \ref{sec:email}~節を見てください。)
	\item 「off」にすると投稿は送られてこなくなります。
	「on」にすると再開できます。
\end{enumerate}

% ----------------------------------------------------------------------------
%en%\subsection{How can I avoid getting duplicate messages? (duplicates option)
%en%\label{sec:nodupes}}
\subsection{メッセージを 重複して 受け取らない
ようにするには (重複オプション)\label{sec:nodupes}}

%en%Mailman can't completely stop you from getting duplicate messages, but it 
%en%can help.  One common reason people get multiple copies of a mail is that 
%en%the sender has used a "group reply" function to send mail to both the list and 
%en%some number of individuals.  If you want to avoid getting these messages,
%en%Mailman can be set to check and see if you are in the \mailheader{To} or
%en%\mailheader{CC} lines of the message.  If your address appears there,
%en%then Mailman can be told not to deliver another copy to you.

Mailman はメッセージの重複を完全に停められるわけではありませんが、
この機能はすこしは役に立つでしょう。
重複して受け取ってしまう主な原因としては、
送信人が「全員に返信」機能を使って、
メールをリストと個人の両方に送ってしまう、というものがあります。
こういったメッセージを受け取りたくない人のために、
Mailman では、あなたのアドレスが \mailheader{To} ヘッダや 
\mailheader{CC} ヘッダに入っていないか調べるように設定できます。
あなたのアドレスがこういったヘッダにあれば、
Mailman があなたにメッセージの控えを送らないようさせることができます。

%en%To turn this on or off using the web interface:
これを Web インタフェイスで有効にしたり無効にしたりするには:
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} 
%en%	for more details on how to do this.)
%en%	\item Scroll down to the bottom of the page to the section marked
%en%	"Avoid duplicate copies of messages?" and change the value accordingly.
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item ページの下のほうの
	「重複したメールを受け取らないようにしますか?」
	というセクションで、設定を好きなように変えます。
\end{enumerate}

%en%This can also be changed for multiple lists at the same time if you are subscribed to 
%en%more than one list on the same domain.  See Section~\ref{sec:global} for 
%en%information about changing settings globally.

おなじドメインの複数のリストに登録しているのなら、
一度にすべてのリストの設定を変えることもできます。
「全部変更」について詳しくは、\ref{sec:global}~節を見てください。

%en%To turn this on or off using the email interface:
これを電子メールインタフェイスで有効にしたり無効にしたりするには:
\begin{enumerate}
%en%   \item Send a mail to \email{LISTNAME-request@DOMAIN} with the command
%en%   \var{set~duplicates~on} or \var{set~duplicates~off}.
   \item \email{LISTNAME-request@DOMAIN} に
   \var{set~duplicates~on} または \var{set~duplicates~off}
   というコマンドを書いたメールを送ります。

%en%   Commands can appear
%en%   in either the body or the subject of the message.  (See
%en%   Section~\ref{sec:email} for more information about sending mail
%en%   commands.)
%en%	\item Set it to "on" to receive list copies of messages already sent
%en%	to you, set it to "off" to avoid receiving these duplicates.
   コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
   (メールコマンドの送りかたについて詳しくは、
   \ref{sec:email}~節を見てください。)
	\item 「on」にすると、あなたに送られたものの控えも送られます。
	「off」にすると重複したものが送られないようにします。
\end{enumerate}


% ----------------------------------------------------------------------------
%en%\subsection{How do I change my subscription address?\label{sec:changeaddress}}
\subsection{登録しているアドレスを変えるには\label{sec:changeaddress}}
%en%To change your subscription address, 
自分の登録アドレスを変えるには、
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} 
%en%	for more details on how to do this.)
%en%	\item In the section marked "Changing your LISTNAME membership information,"
%en%	enter your new address.
%en%	\item If you wish to change your address for all subscriptions using the 
%en%	old address, select the "Change globally" box.  If you have subscriptions
%en%	under another address or for lists on a different domain, these will have
%en%	to be done separately. See Section~\ref{sec:global} for more
%en%	information about changing settings globally.
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「あなたの LISTNAME 会員アドレス変更」というセクションで、
	あなたの新しいアドレスを入力します。
	\item 元のアドレスで登録しているすべてのリストの登録アドレスを
	変えたいのなら、「全部変更」チェックボックスを選択します。
	ほかのアドレスでの登録があったり、ほかのドメインのリストに
	登録しているアドレスについては、別々に変更しなければなりません。
	「全部変更」について詳しくは、\ref{sec:global}~節を見てください。
\end{enumerate}

%en%There is no special way to do this from the email interface, but you can 
%en%subscribe and unsubscribe for more or less the same effect.  (See 
%en%Sections~\ref{sec:subscribe} and \ref{sec:unsubscribe} for more information
%en%on subscribing and unsubscribing.)

電子メールインタフェイスでは同じことをやる方法はありませんが、
新しいアドレスで入会しておいて元のアドレスを退会すれば、
おおむね同じ結果になります。
(入会と退会について詳しくは
\ref{sec:subscribe}~節と \ref{sec:unsubscribe}~節を見てください。)

% ----------------------------------------------------------------------------
%en%\subsection{How do I stop or start getting copies of my own posts? (myposts
%en%	option)\label{sec:getown}}
\subsection{投稿の控え を 受け取らない
ようにしたり、
受け取るようにしたりするには (控えなしオプション)\label{sec:getown}}
%en%By default in Mailman, you get a copy of every post you send to the list.  
%en%Some people like this since it lets them know when the post has gone through
%en%and means they have a copy of their own words with the rest of a discussion, 
%en%but others don't want to bother downloading copies of their own posts.
Mailman では、ふつうは自分が投稿したものの控えも送られてきます。
そうなっていたほうがいいという人もいます。
投稿が無事に送られたかどうか分かるし、
自分の意見を議論の一部としていっしょに保存しておけるからだそうです。
しかし、自分が投稿したものをわざわざまたダウンロードさせられるのを
嫌がる人もいます。

%en%\note{This option has no effect if you are receiving digests.}
\note{まとめ読みで受け取っているときは、このオプションは効きません。}

%en%You may also want to see Section~\ref{sec:getack}, which discusses 
%en%acknowledgement emails for posts sent to the list.

\ref{sec:getack}~節では、
投稿に対して受領メールを送ってもらう方法を説明しているので、
そちらも見ておくとよいでしょう。

%en%To set this using the web interface:
これを Web インタフェイスで設定するには:
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} 
%en%	for more details on how to do this.)
%en%	\item Look for the section marked "Receive your own posts to the list?"  
%en%	Set it to "Yes" to receive copies of your own posts, and  "No" to avoid
%en%	receiving them.
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「重複したメールを受け取らないようにしますか?」
	というセクションを探し、自分の投稿の控えを送ってもらうなら「はい」、
	送ってもらわないようにするなら「いいえ」に設定します。
\end{enumerate}

%en%To set this using the email interface:
これを電子メールインタフェイスで設定するには:
\begin{enumerate}
   \item \email{LISTNAME-request@DOMAIN} に
   \var{set~myposts~on} または \var{set~myposts~off}.
   というコマンドを書いたメールを送ります。

%en%   Commands can appear
%en%   in either the body or the subject of the message.  (See
%en%   Section~\ref{sec:email} for more information about sending mail
%en%   commands.)
%en%	\item Set it to "on" to receive copies of your own posts, and "off"
%en%	to avoid receiving them.
   コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
   (メールコマンドの送りかたについて詳しくは、
   \ref{sec:email}~節を見てください。)
	\item 「on」にすると自分の投稿の控えも送られるようになります。
	「off」にすると控えが送られなくなります。
\end{enumerate}


% ----------------------------------------------------------------------------
%en%\subsection{How can I get Mailman to tell me when my post has been received
%en%by the list? (ack option)\label{sec:getack}}
\subsection{投稿がリストに届いたことを Mailman から知らせて
もらうようにするには (受領オプション)\label{sec:getack}}

%en%On most lists, you will simply receive a copy of your mail when it has gone
%en%through the list software, but if this is disabled (See 
%en%Section~\ref{sec:getown}), your list mail delivery is disabled (See
%en%Section~\ref{sec:nomail}), you are not subscribed to that topic (See
%en%Section~\ref{sec:sometopic}) or you
%en%simply want an extra acknowledgement from the system, this option may
%en%be useful to you.

たいていのリストでは、投稿したメールがメーリングリストシステムを通過すると
投稿したあなたにも同じものが送られてきます。
しかし、送られないようにしているとき
(\ref{sec:getown}~節を見てください)、
配送を停めているとき
(Section~\ref{sec:nomail}~節を見てください)、
その投稿の話題を購読しないようにしているとき 
(\ref{sec:sometopic}~節を見てください)、
あるいはその他の理由で投稿が届いたことを特に知りたいときには、
このオプションが役立つでしょう。

%en%\note{If you are not subscribed to the list, this option cannot be used.  
%en%You must either check the archives yourself (if the list has public archives),
%en%ask someone who is subscribed to the list, or subscribe to use this option.}

\note{あなたがリストに入会していないのなら、
このオプションは使えません。
そういうときは、リストの保存書庫を見て確認する
(リストの保存書庫が公開されているのなら) か、
誰かリストの参加者に聞いて確認するか、
あるいはリストに入会してこのオプションを使えるようにするか、
のいずれかでしょう。}

%en%To set this using the web interface:
これを Web インタフェイスで設定するには:
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} 
%en%	for more details on how to do this.)
%en%	\item Look for the section marked "Receive acknowledgement mail when you
%en%	send mail to the list?"  
%en%	Set it to "Yes" to receive a mail letting you know your post has been
%en%	received, and  "No" to avoid receiving such an acknowledgement.
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「あなたがリストに投稿したとき, 受領メールが 必要ですか?」
	というセクションを探し、
	自分の投稿が届いたことを知らせてもらうのなら「はい」、
	知らせてもらわないようにするなら「いいえ」に設定します。
\end{enumerate}

%en%To set this using the email interface:
これを電子メールインタフェイスで設定するには:
\begin{enumerate}
%en%   \item Send a mail to \email{LISTNAME-request@DOMAIN} with the command
%en%   \var{set~ack~on} or \var{set~ack~off}.
   \item \email{LISTNAME-request@DOMAIN} に
   \var{set~ack~on} または \var{set~ack~off}
   というコマンドを書いたメールを送ります。

%en%   Commands can appear
%en%   in either the body or the subject of the message.  (See
%en%   Section~\ref{sec:email} for more information about sending mail
%en%   commands.)
%en%	\item Set it to "on" if you wish to receive mail letting you know your 
%en%	post has been received, and  "off" to avoid receiving such an 
%en%	acknowledgement.
   コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
   (メールコマンドの送りかたについて詳しくは、
   \ref{sec:email}~節を見てください。)
	\item 投稿が届いたことを知らせてもらうのなら「on」、
	知らせてもらわないのなら「off」にします。
\end{enumerate}

% ----------------------------------------------------------------------------
%en%\subsection{I don't seem to be getting mail from the lists.  What should
%en%	I do?}
\subsection{どのリストからも メールが 届かないようです。
どうしたら いいのでしょうか}
%en%There are a few common reasons for this:
届かない理由としては、主につぎのようなことが考えられます:
\begin{itemize}
%en%	\item No one has sent any mail to the list(s) you're on for a little while.
	\item あなたが入っているどのリストにも、
	ここしばらく誰も投稿していない。

%en%	To check if this is the case, try visiting the archives of the list 
%en%	(assuming that the list has archives).  If the list has no archives, you
%en%	may have to ask another subscriber.  (See Section~\ref{sec:web} for help
%en%	in finding the list archives.)

	これを確かめるには、それぞれのリストの保存書庫
	(保存書庫があるとして) を見てまわるとよいでしょう。
	リストに保存書庫がないときは、
	ほかのリスト参加者に聞いてみるといいかもしれません。
	(リストの保存書庫の探しかたは
	\ref{sec:web}~節を見てください。)

%en%	\note{Generally, it is considered 
%en%	impolite to send test messages to the entire list.
%en%	If you feel a need to test that the list is working and for some reason you
%en%	cannot simply compose a regular message to the list, it is less disruptive 
%en%	to send a help message to
%en%	the list request address (LISTNAME-request@DOMAIN) to see if that works,
%en%	or to contact the list 
%en%	administrator (LISTNAME-owner@DOMAIN) to ask if the list is working.}

	\note{リストに投稿できるかどうか調べるためだけに
	内容のないメッセージを送ってみるというのは、
	一般に、無作法な振舞いとされます。
	リストが稼働しているかどうか調べてみたいが
	リストに投稿するのにふさわしいものを書けそうにない、
	というときは、
	リストの申請アドレス (LISTNAME-request@DOMAIN) に
	help のメッセージを送って稼働していることを確かめるか、
	あるいは、リスト管理者 (LISTNAME-owner@DOMAIN) に連絡をとって
	リストが稼働しているかどうか尋ねるのが、無難なやりかたです。}
	
%en%	\item You were bouncing mail and have had mail delivery (temporarily) 
%en%	disabled by the list software.

	\item あなたからエラーメッセージが返ってくるので、
	メーリングリストシステムによってあなたへの配送が
	(一時的に) 停止されている。

%en%	If your mail provider "bounces" too many messages (that is, it tells
%en%	Mailman that the message could not be delivered)
%en%	Mailman eventually stops trying to send you mail.  This feature allows
%en%	Mailman to gracefully handle addresses which no longer exist (for example,
%en%	the subscriber has found a new internet service provider and forgot to 
%en%	unsubscribe the old address), as well
%en%	as addresses which are temporarily out-of-service (for example, the 
%en%	subscriber has used up all of the allotted space for his or her email
%en%	account, or the subscriber's mail provider is experiencing difficulties).

	あなたのメールアドレスを管理している組織が、
	メッセージをあまりにたびたびエラーにする
	(Mailman に対してメッセージが送れないと知らせる)
	と、Mailman はある時点で、あなたにメールを送るのを
	やめてしまうようになっています。
	この機能によって Mailman では、なくなってしまったアドレス
	(たとえば、ある参加者がインターネットサービスプロバイダを替えたが、
	古いアドレスを退会させるのを忘れた、など) や、
	一時的に使えなくなっているアドレス (たとえば、
	ある参加者が自分の電子メールアドレス用のスペースを
	使い切ってしまったとか、参加者のメールアドレスを管理している組織で
	トラブルが起こっているとか)
	を、うまく処理できるようになっています。

%en%	Even if you are unaware of any difficulties with your mail provider, it 
%en%	is a good idea to check this.  Some popular webmail providers and 
%en%	internet servers are not as reliable as one might assume, nor is the
%en%	internet as a whole.  You may want to also send yourself a test message
%en%	from another account or ask a friend to send you a test message to make
%en%	sure your subscribed address is working.

	自分の電子メールアドレスを管理している組織で
	トラブルが起こっているとは思っていなくても、
	まずそれを確かめてみたほうがいいです。
	有名な Web メールサービス業者やインターネットサービスでも、
	思ったより信頼性が低いことがありますし、
	インターネットというのは全体としてそういうものです。
	ほかのメールアカウントを持っているのなら、
	そちらから自分にテストメールを送ってみればよいでしょう。
	あるいは、知人に頼んでテストメッセージを送ってもらうのもよいでしょう。
	とにかくそうやって、自分の登録アドレスがちゃんと使えるかどうか
	確かめます。

%en%	To check if this may be the reason you are not receiving messages, log in 
%en%	to the your options page (See
%en%	Section~\ref{sec:web} for more details on how to do this) and 
%en%	look at your options.  There should be one marked "Mail Delivery" --
%en%	if it is set to "Disabled," set it to "Enabled" to start receiving mail
%en%	again. (For more instructions on disabling or enabling mail delivery,
%en%	see Section~\ref{sec:nomail}.)

	自分への配送が停止されているせいで
	送られてこないのかどうかを確かめるには、
	あなたの会員オプションページにログイン
	(どうしたらよいかは \ref{sec:web}~節を見てください)
	して、自分のオプションを見ます。
	「メール配送」というセクションがありますが、
	ここが「停止」になっているのなら、「有効」に設定すれば
	またメールを受け取れるようになります。
	(メール配送を停止したり有効にしたりする手順について詳しくは
	\ref{sec:nomail}~節を見てください。)

%en%	\note{Even if you have not been disabled at the time you check, you could be
%en%	bouncing messages and not have reached the threshold for your 
%en%	subscription to be disabled.  You may need to check again.}

	\note{調べたときに「停止」になっていないとしても、
	あなたのアドレスからはエラーメッセージが送られており、
	それがまだ配送停止になるほど多くないだけかもしれません。
	しばらくしてからまた調べたほうがよいでしょう。}

%en%	\item There is a delay or break in the networks between you and the 
%en%	list server.

	\item あなたとメーリングリストサーバとの間で通信に遅れが出ているか、
	通信が不通になっている。

%en%	No matter what many of us would like, the internet is not 100\% 
%en%	reliable, nor is it always fast.  Sometimes, messages simply take a long 
%en%	time to get to you.  Try to be patient, especially if the server is far 
%en%	(in terms of networks, not geography, although often one implies the other)
%en%	from your internet service provider.

	インターネットは、わたしたちの多くが思っているほど、
	100\% 信頼できるものでも、
	高速なものでもありません。
	ときには、メッセージがあなたに届くのに長い時間がかかることもあります。
	特に、メーリングリストのサーバが
	あなたのインターネットサービスプロバイダから遠い
	(コンピュータネットワークの上でのことで、地理的な意味でではありません。
	前者はときには後者の意味も含みますが)
	ときには、すこし辛抱して待ってみてください。

%en%	To check if this might be causing your problem, you can try pinging
%en%	the list server or tracing the route between you and it.  (Instructions
%en%	on how to do this varies from platform to platform, so you may want to 
%en%	use a search engine to find those appropriate for you.)

	これが原因かどうか確かめるには、
	メーリングリストサーバに ping を送ったり、
	そのサーバとあなたのコンピュータとの間のルートを
	トレースしたりしてみることができます。
	(どうしたらよいかは、使っているシステムによってさまざまですので、
	検索エンジンなどであなたに合ったやりかたを調べるとよいでしょう。)

%en%	\item The Mailman installation on the list server is not functioning or
%en%	not functioning properly.

	\item そのメーリングリストサーバに入っている Mailman
	がまったく動作していないか、正しく動作していない。
	
%en%	To test if this is a case, try visiting the list's web interface and 
%en%	try sending a message to \email{LISTNAME-request@DOMAIN} with the command 
%en%	"\var{help}" (without the quotes) in the \mailheader{Subject}.  If 
%en%	neither of these works after a reasonable length of time, this may be
%en%	the problem.  You may wish to contact either the list or site 
%en%	administrator(s).

	これが原因かどうか調べるには、
	まず、リストの Web ページへ行ってみます。
	また、\email{LISTNAME-request@DOMAIN} に、\mailheader{Subject}
	(件名) に「\var{help}」(鍵括弧は付けない) 
	といった簡単なコマンドを書いたメッセージを送ってみます。
	少し待っても、どちらもなにも起こらないようなら、
	原因はこれです。
	リストかサイトの管理者に連絡をとるとよいでしょう。
\end{itemize}


% ============================================================================
%en%\section{Digests}
\section{まとめ読み}
% ----------------------------------------------------------------------------
%en%\subsection{How can I start or stop getting the list posts grouped into one 
%en%big email? (digest option)\label{sec:digest}}
\subsection{リストの投稿 を まとめて
受け取ったり、一通ずつ受け取ったりするには
(まとめ読みオプション)\label{sec:digest}}

%en%Groups of posts are called "digests" in Mailman.  Rather than get messages
%en%one at a time, you can get messages grouped together.  On a moderately busy
%en%list, this typically means you get one email per day, although it may be
%en%more or less frequent depending upon the list.

Mailman では、投稿をまとめたものを「まとめ読み」と言っています。
メッセージを一通ずつ受け取るのではなく、
一度にまとめて受け取ることができます。
それなりに投稿量の多いリストでは、だいたい一日に 1 度、メールが送られます。
リストによって、もっと度々だったり、少なかったりします。

%en%You may also want to look at Section~\ref{sec:MIME} which discusses MIME
%en%and plain text digests.

\ref{sec:MIME}~節では
MIME のまとめ読みと平文のまとめ読みについて説明しています。
そちらも見るとよいでしょう。

%en%To turn digest mode on or off using the web interface,
Web インタフェイスでまとめ読みモードにしたり、やめたりするには:
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} 
%en%	for more details on how to do this.)
%en%	\item Look for the section marked "Set Digest Mode."  
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「まとめ読みモードに設定」というセクションを探します。

%en%	Set it to "On" to 
%en%	receive messages bundled together in digests.  Set it to "Off" to 
%en%	receive posts separately.

	まとめ読みにまとめて送ってもらうのなら「有効」、
	一通ずつ送ってもらうのなら「無効」に設定します。
\end{enumerate}

%en%To turn digest mode on or off using the email interface,
電子メールインタフェイスでまとめ読みモードにしたり、やめたりするには:
\begin{enumerate} 
%en%   \item Send a mail to \email{LISTNAME-request@DOMAIN} with the command
%en%   \var{set~digest~plain} or \var{set~digest~mime} or \var{set~digest~off}.
   \item \email{LISTNAME-request@DOMAIN} に
   \var{set~digest~plain} または \var{set~digest~mime} 
   または \var{set~digest~off}
   というコマンドを書いたメールを送ります。
   
%en%   Commands can appear
%en%   in either the body or the subject of the message.  (See
%en%   Section~\ref{sec:email} for more information about sending mail
%en%   commands.)
%en%   \item Set it to "off" if you wish to receive individual posts separately,
%en%	and to "plain" or "mime" to receive posts grouped into one large mail.
%en%	See Section~\ref{sec:MIME} for more information on plain versus MIME
%en%	digests.
   コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
   (メールコマンドの送りかたについて詳しくは、
   \ref{sec:email}~節を見てください。)
   \item 投稿を一通ずつ送ってもらうのなら「off」、
     ひとつの大きなメールにまとめて送ってもらうのなら
     「plain」か「mime」にします。
     平文のまとめ読みと MIME のまとめ読みの違いについては
     \ref{sec:MIME}~節を見てください。
\end{enumerate}


% ----------------------------------------------------------------------------
%en%\subsection{What are MIME and Plain Text Digests?  How do I change which one
%en%I get? (digest option)\label{sec:MIME}}
\subsection{MIME のまとめ読みと 平文のまとめ読み
とは。まとめ読みの種類を変えるには (まとめ読みオプション)\label{sec:MIME}}

%en%MIME is short for Multipurpose Internet Mail Extensions.  It is used to 
%en%send things by email which are not necessarily simple plain text.  (For 
%en%example, MIME would be used if you were sending a picture of your dog to 
%en%a friend.)  

MIME は「多用途インターネットメール機能拡張」
(Multipurpose Internet Mail Extensions) の略です。
これは、単純なプレインテキストに限らずさまざまなデータを
電子メールで送るのに使います。
(たとえば、飼い犬の写真を友達に送るようなときは、MIME
を使っています。)

%en%A MIME digest has each message as an attachment inside the message, along
%en%with a summary table of contents.  

MIME のまとめ読みでは、それぞれのメッセージはメッセージ内の添付となっていて、
目次がついています。

%en%A plain text digest is a simpler form of digest, which should be readable 
%en%even in mail readers which don't support MIME.  The messages are simply put 
%en%one after the other into one large text message.

平文のまとめ読みはより単純なもので、
メールソフトが MIME に対応していなくても読みやすくなっています。
メッセージが順番に並んでいるだけの、
大きなテキストメッセージになっています。

%en%Most modern mail programs do support MIME, so you only need to choose 
%en%plain text digests if you are having trouble reading the MIME ones.

最近は多くのメールソフトが MIME に対応していますから、
MIME のまとめ読みがうまく読めないときだけ、
平文のほうにすればいいでしょう。

%en%\note{This option has no effect if you are not receiving mail bunched
%en%as digests.  (See Section~\ref{sec:digest} for more information on 
%en%receiving mail as digests.)}

\note{まとめ読みにまとめて送ってもらっていないときは、
このオプションは効きません。
(まとめ読みで送ってもらうには詳しくは
\ref{sec:digest}~節を見てください。)}

%en%To set your digest type using the web interface:
まとめ読みの種類を Web インタフェイスで設定するには:
\begin{enumerate}
%en%   \item Log in to your member options page.  (See Section~\ref{sec:web}
%en%   for more details on how to do this.)
%en%   \item Look for the section marked "Get MIME or Plain Text Digests?."
   \item あなたの会員オプションページにログインします。
   (どうしたらよいかは \ref{sec:web}~節を見てください。)
   \item 「まとめ読みのメールを平文で受けますか？ MIMEの添付で受けますか?」
   というセクションを探します。

%en%	Set it to "MIME" to receive digests in MIME format, or "Plain text" to 
%en%	receive digests in plain text format. 
	MIME の形式でまとめ読みを送ってもらうときは「MIME」、
	平文の形式でまとめ読みを送ってもらうときは「平文」に設定します。
\end{enumerate}

%en%This can also be changed for multiple lists at the same time if you are subscribed to 
%en%more than one list on the same domain.  See Section~\ref{sec:global} for 
%en%information about changing settings globally.

おなじドメインの複数のリストに登録しているのなら、
一度にすべてのリストの設定を変えることもできます。
「全部変更」について詳しくは、\ref{sec:global}~節を見てください。

%en%To set your digest type using the email interface,
まとめ読みの種類を電子メールインタフェイスで設定するには:
\begin{enumerate}
%en%   \item Send a mail to \email{LISTNAME-request@DOMAIN} with the command
%en%   \var{set~digest~plain} or \var{set~digest~mime}.
   \item \email{LISTNAME-request@DOMAIN} に
   \var{set~digest~plain} または \var{set~digest~mime} 
   というコマンドを書いたメールを送ります。

%en%   Commands can appear
%en%   in either the body or the subject of the message.  (See
%en%   Section~\ref{sec:email} for more information about sending mail
%en%   commands.)
%en%   \item Set it to "plain" to get posts bundled into a plain text digest,
%en%	or "mime" to get posts bundled together into a MIME digest.
   コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
   (メールコマンドの送りかたについて詳しくは、
   \ref{sec:email}~節を見てください。)
   \item 投稿を平文のまとめ読みにまとめて送ってもらうのなら「plain」、
   MIME のまとめ読みにまとめて送ってもらうのなら「mime」にします。
\end{enumerate}

% ----------------------------------------------------------------------------
\section{Mailing list topics\label{sec:topics}}

Some lists are set up so that different topics are handled by Mailman.
For example, the courses list on Linuxchix.org is a discussion list for
courses being run by linuxchix members, and often there are several courses
being run at the same time.  
(eg: Networking for beginners, C programming, \LaTeX ~document mark up.)  
Each of the courses being run is a separate topic on the list so that people
can choose only to receive the course they want to take.

These
topics must be configured by the list administrator, but it is the
responsibility of each poster to make sure that their post is put with 
the correct topic.  Usually, this means adding a tag of some type to the 
subject line (eg: [Networking] What type of cables do I need?) or making
sure the \mailheader{Keywords} line has the right information.  (By default, 
you can put a \mailheader{Keywords} section in the beginning of the body
of your message, but this can be configured by your list administrator.)
Note that these tags are case-insensitive.

% ----------------------------------------------------------------------------
\subsection{How do I make sure that my post has the right 
	topic?\label{sec:posttopic}}

When a list administrator defines a topic, he or she sets three things:
\begin{itemize}
	\item a topic name
	\item a regular expression (regexp)
	\item a description
\end{itemize}

You can view this information by logging in to your member options page. 
 (See Section~\ref{sec:web} for more details on how to do this.) and 
clicking on the "details" link for any topic that interests you.

To post on a given topic, you need to make sure that the 
\mailheader{Keywords} or \mailheader{Subject} headers in a message  
match the \emph{regular expression} for that topic.  
Regular expressions can actually be fairly complex, so you may want to 
just ask the list administrator if you don't know how to make
heads or tails of the expression given.  

Most Mailman topic expressions will be fairly simple regular expressions, so 
in this document we will simply give you some common examples.  Regular 
expressions are a bit too complex to teach in a few lines here, so if you
really want to understand how the regular expressions work, you should
find a tutorial or reference elsewhere.  (For example, DevShed has a decent
tutorial at 
\url{http://www.devshed.com/Server_Side/Administration/RegExp/})  

Here are some examples of possible regular expressions and matching lines:

\begin{tableii}{l|l}{}{Regular expression}{Matching lines}
	\lineii{zuff}{Keywords: zuff}
	\lineii{zuff}{Keywords: ZUFF}
	\lineii{zuff}{Keywords: Zuff}
	\lineii{zuff}{Keywords: amaryllis, zuff, applesauce}
	\lineii{zuff}{Subject: [zuff] Do you have the right stuff for zuff?}
	\lineii{zuff}{Subject: Do you have the right stuff for zuff?}
	\lineii{zuff}{Subject: What is zuff?}
\hline
	\lineii{\textbackslash[zuff\textbackslash]}{Keywords: [zuff]}
	\lineii{\textbackslash[zuff\textbackslash]}{Subject: [zuff]	Do you have the right stuff?}
	\lineii{\textbackslash[zuff\textbackslash]}{Subject: Online zuff tutorials (was Re: [zuff] What is zuff?)}
\end{tableii}

A few notes:
\begin{itemize}
	\item The matching is case-insensitive, so if zuff matches, so will ZUFF,
	 zuFF, and any other variations in capitalization.
	\item Some characters have special meaning in a regular expression, so
	to match those characters specifically, they must be "escaped" with a 
	backslash (\textbackslash).  As you can see in the above example, 
	[ and ] are such characters.  (Others include ".", "?", and "*").  
	The backslash is also used for other things (I wasn't kidding about 
	regular expressions being complex: consult other documentation
	for details about other uses of the backslash character), but this 
	is the most likely use in a topic expression.
\end{itemize}

% ----------------------------------------------------------------------------
\subsection{How do I subscribe to all or only some topics on a 
	list?\label{sec:sometopic}}

If topics have been set up by your mailing list administrator, you can 
choose to subscribe to only part of a list by selecting the topics you
want to receive.

If you wish to get all messages sent to the list, make sure you 
are not subscribed to any topics.

\begin{enumerate}
	\item Log in to your member options page.  (See Section~\ref{sec:web} 
	for more details on how to do this.)
	\item Look for the section marked "Which topic categories would you like 
	to subscribe to?" 

	If any topics are defined, you can select those you wish.  If you do
	not select any topics of interest, you will receive all posts 
	sent to the list.
\end{enumerate}

You probably also want to look at Section~\ref{sec:notopic} which discusses
changing your settings for messages where no topic is set.

% ----------------------------------------------------------------------------
\subsection{How do I get or avoid getting messages with no topic set?
\label{sec:notopic}}
If you wish to get all messages sent to the list, make sure you are 
not subscribed to any specific topic.  (See Section~\ref{sec:sometopic}.)  

If you are only subscribed to some topics, you can either choose to either
receive or not receive messages with no topic set, much the way you can 
choose to subscribe only to certain topics.

To change this setting,
\begin{enumerate}
	\item Log in to your member options page.  (See Section~\ref{sec:web} 
	for more details on how to do this.)
	\item Look for the section marked "Do you want to receive message that do 
	not match any topic filter?"

	If you wish to receive messages with no topic set, select "Yes."  If you
	do not wish to receive such messages, choose "No."
\end{enumerate}

This setting has no effect if you are not subscribed to any topics.

% ============================================================================
%en%\section{Setting other options}
\section{そのほかのオプション}

% ----------------------------------------------------------------------------
%en%\subsection{Change Globally?  Set Globally? What does that mean?
%en%	\label{sec:global}}
\subsection{「全部変更」や「全部設定」の意味
	\label{sec:global}}

%en%For some of the options given in your member options page, there is a 
%en%tick-box which says "Change Globally" or "Set Globally."  
%en%This means that if you change this
%en%option, you can also have the change made for all your other list 
%en%subscriptions with the same address to lists on the same domain.  
%en%This can be handy if, for example, you 
%en%want to make sure all your passwords are the same, or you are going on 
%en%vacation and want to turn off mail delivery from all the lists.

会員オプションページにあるいくつかのオプションには、
「全部変更」や「全部設定」というチェックボックスがあります。
これは、オプションを変更したときに、同じドメインのリストで
同じアドレスで登録しているリストについてもすべて変更する、
という意味です。
これは、つぎのようなときに便利です:
たとえば、パスワードを全部同じにしたいとき。
またたとえば、休暇に入るのですべてのリストのメール配送を
停止しておきたいとき。

% ----------------------------------------------------------------------------
%en%\subsection{How do I change my name as Mailman knows it?
%en%	\label{sec:changename}}
\subsection{Mailman に登録してある名前を変えるには
	\label{sec:changename}}

%en%To change your subscription name, 
登録してある名前を変えるには、
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} 
%en%	for more details on how to do this.)
%en%	\item In the section marked "Changing your LISTNAME membership information,"
%en%	enter your new name in the appropriate box.
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「あなたの LISTNAME 会員アドレス変更」というセクションで、
	あなたの新しい名前を入力します。
\end{enumerate}

%en%This can also be changed for multiple lists at the same time if you are subscribed to 
%en%more than one list on the same domain.  See Section~\ref{sec:global} for 
%en%information about changing settings globally.
おなじドメインの複数のリストに登録しているのなら、
一度にすべてのリストの設定を変えることもできます。
「全部変更」について詳しくは、\ref{sec:global}~節を見てください。

%en%\note{You do not need to have a subscription name set.}
\note{参加者の名前は、必ず設定しなければならないわけではありません。}

% ----------------------------------------------------------------------------
%en%\subsection{How do I set my preferred language?}
\subsection{使う言語を変えるには}

%en%Mailman is available with many different languages.
%en%(For a complete listing see \url{http://mailman.sourceforge.net/i18n.html}.)  This means that, if your list has
%en%other languages enabled, you may be able to have the web interface, etc. in a 
%en%language of your choice.  

Mailman では、多くの異なった言語が使えます。
(完全な一覧は \url{http://mailman.sourceforge.net/i18n.html}
を見てください。)  つまり、リストで他の言語が使えるようになっていれば、
あなたは Web インタフェイスなどを自分の選んだ言語で使えるのです。

%en%\note{This does NOT necessarily mean that all the posts sent to the list will 
%en%be in the language you selected.  Only the pre-prepared texts presented by 
%en%Mailman will be affected by this setting.  Posts are in whatever language the
%en%poster uses.}

\note{リストへの投稿が全部あなたの選んだ言語になる、
ということではありません。
あらかじめ用意されている Mailman の文章が変わるだけです。
投稿は、それぞれの投稿者が使っている言語のままです。}

%en%Your preferred language is set when you subscribe (see 
%en%Section\ref{sec:subscribe}), and can be changed later if the list supports
%en%more than one language.  

使う言語は、あなたが入会 (\ref{sec:subscribe}~節を見てください)
したときに設定されていますが、リストが複数の言語に対応していれば、
後で変えることができます。

%en%To change your preferred language in Mailman,
Mailman で使う言語を変えるには、
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} for 
%en%   instructions on how to do this.)
%en%	\item Go to the section marked "What language do you prefer?" and choose
%en%	the appropriate language from the drop-down list.  If there is no
%en%	drop-down list of languages, the list you are on probably only supports
%en%	one language.  
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「どの言語を使いますか?」というセクションへ行き、
	ドロップダウンリストで好きな言語を選択します。
	言語のドロップダウンリストがないときは、
	あなたの入っているリストはたったひとつの言語にしか
	対応していないということです。
\end{enumerate}

%en%If your list does not support the language you would prefer to use, you may
%en%contact the list administrator (LISTNAME-owner@DOMAIN) to see if it can be 
%en%added, but remember that this may mean some work that the list and/or site 
%en%administrator(s) do not have time or the ability to do.  

リストがあなたの使いたい言語に対応していないときは、
リスト管理者 (LISTNAME-owner@DOMAIN) に連絡をとって、
その言語を追加してもらうよう頼むこともできます。
ただし、覚えておいていただきたいのですが、これには少し
作業が必要になるので、リスト管理者やサイト管理者のほうで
作業をできるだけの時間がとれないこともありえます
\footnote{[訳注] リスト管理者は、その言語で案内ページや
「ようこそ」メールの内容などを用意しなければなりません。
また、Mailman にその言語のための翻訳データが組み込まれていないときは、
サイト管理者は Mailman に翻訳データを追加しなければなりません。}。

%en%If your language of choice is not available because no translation
%en%exists for Mailman, please consider volunteering your time as a translator.
%en%For more information you may want to consult the mailman-i18n mailing 
%en%list at \url{http://mail.python.org/mailman/listinfo/mailman-i18n}.
%en%(i18n is a common short-hand for "internationalization" because the word starts 
%en%with an i, ends with an n, and has 18 letters in between.  If you mumble a bit,
%en%i18n even sounds a bit like "internationalization.")

あなたの言語が Mailman に翻訳がないために使えない、ということがあれば、
あなたの時間を翻訳のために使うことも考えていただけると、
ありがたいです。
詳しい情報は、\url{http://mail.python.org/mailman/listinfo/mailman-i18n}
の mailman-i18n メーリングリストで得られます。
(i18n というのは、「国際化」(internationalization) の略号としてよく使われます。
最初の i と最後の n の間に 18 文字あるので、こう書きます。
発音もなんとなく「internationalization」に似ていますし。)

% ----------------------------------------------------------------------------
%en%\subsection{How do I avoid having my name appear on the subscribers list?
%en%	(the hide option)\label{sec:nolist}}
\subsection{会員名簿 に 名前を出さない
ようにするには (隠れオプション)\label{sec:nolist}}

%en%If you do not want to have your email address show up on the subscriber list
%en%for any reason, you can opt to have it concealed.

なんらかの理由で会員名簿に自分の電子メールアドレスを出したくないのなら、
隠すこともできます。

%en%Common reasons for doing this include avoiding unsolicited bulk email (spam).  
%en%By default, the subscribers list is obscured to hinder spam harvesters,
%en%but if you feel this is insufficient it's easy enough to remove address
%en%from the subscriber list given in the information pages or by email request.
%en%(Note that this does not conceal your address from the list administrators.)
%en%You may wish to see Section~\ref{sec:antispam} for more information on what
%en%Mailman can do to help avoid spam.  

主な理由のひとつに、受信者の承諾を得ずに大量に送られる電子メール (スパム)
の防止があります。
初期状態では、会員名簿のアドレスは、スパム送信先アドレス収集ソフトウェア
から隠すためにぼやかしてあります。
これでは不十分だと思うのなら、案内ページや電子メールコマンドで
取得できる会員名簿からアドレスを消してしまうのが簡単です
\footnote{[訳注] 会員名簿を会員や管理者以外に公開していないメーリングリストで、
他の会員が十分信用できるのなら、
スパム防止のために会員名簿からアドレスを消す必要はないです。}。
(なお、このようにしても、リスト管理者はあなたのアドレスを見ることができます。)
スパムに対して Mailman ではどんな対策ができるかについて詳しくは、
\ref{sec:antispam}~節を見るとよいでしょう。

%en%To change this setting using the web interface:
この設定を Web インタフェイスで変えるには:
\begin{enumerate}
%en%	\item Log in to your member options page.  (See Section~\ref{sec:web} for 
%en%   instructions on how to do this.)
%en%	\item Go to the section marked "Conceal yourself from subscriber list?" and
%en%	choose "Yes" to hide your name from the list, or "No" to allow your name
%en%	to appear on the list.
	\item あなたの会員オプションページにログインします。
	(どうしたらよいかは \ref{sec:web}~節を見てください。)
	\item 「会員名簿にあなたを出さないようにしますか?」
	というセクションへ行きます。
	名簿に名前を載せないときは「はい」、
	載せるときは「いいえ」を選びます。
\end{enumerate}

%en%To change this setting using the email interface:
この設定を電子メールインタフェイスで変えるには:
\begin{enumerate} 
%en%   \item Send a mail to \email{LISTNAME-request@DOMAIN} with the command
%en%   \var{set~hide~on} or \var{set~hide~off}.
   \item \email{LISTNAME-request@DOMAIN} に
   \var{set~hide~on} または \var{set~hide~off}
   というコマンドを書いたメールを送ります。

%en%   Commands can appear 
%en%   in either the body or the subject of the message.  (See
%en%   Section~\ref{sec:email} for more information about sending mail
%en%   commands.)
%en%   \item Set it to "on" to conceal your email address from the membership
%en%	list, or "off" to stop concealing your address.
   コマンドはメッセージの本文と subject (件名) のどちらにでも書けます。
   (メールコマンドの送りかたについて詳しくは、
   \ref{sec:email}~節を見てください。)
   \item あなたの電子メールアドレスを会員名簿で隠すのなら「on」、
   隠すのをやめるのなら「off」にします。
\end{enumerate}

% ============================================================================
%en%\section{Other common questions}
\section{よくある質問}

% ----------------------------------------------------------------------------
%en%\subsection{How do I view the list archives?}
\subsection{リストの保存書庫を見るには}
%en%If the list has archives, they can be viewed by going to a web page address.
%en%This address usually linked from the list information page and can be found in 
%en%the \mailheader{List-Archive} of every list message unless your list 
%en%administrator has disabled these headers.  (Many mail programs hide the 
%en%\mailheader{List-Archive} mail header, so you may have to tell your 
%en%mail program to allow you to view full headers before you will be able to 
%en%see it.)
リストに保存書庫があるのなら、
その Web ページへ行けば見ることができます。
このページはふつうはリスト案内ページからリンクされていますし、
管理者が無効にしていなければリストのそれぞれのメッセージの
\mailheader{List-Archive}
ヘッダに URL が表示されます。
(多くのメールソフトが
\mailheader{List-Archive}
ヘッダを隠すので、
こういったヘッダを見たければすべてのヘッダを表示しておくように
メールソフトを設定しなければならないかもしれません。)

%en%Public archives usually have addresses of the form 
%en%\url{http://WEBSERVER/pipermail/LISTNAME/} and private archives usually
%en%have addresses of the form \url{http://WEBSERVER/mailman/private/LISTNAME}.

公開されている保存書庫は、ふつう
\url{http://WEBSERVER/pipermail/LISTNAME/}
という形の URL で、
公開が限定されている保存書庫は、ふつう
\url{http://WEBSERVER/mailman/private/LISTNAME}
という形の URL になります。

%en%See Section~\ref{sec:web} for more information on finding the addresses of a
%en%list.
リストの Web ページの探しかたについて詳しくは、
\ref{sec:web}~節を見てください。

% ----------------------------------------------------------------------------
%en%\subsection{What does Mailman do to help protect me from unsolicited bulk email
%en%(spam)?\label{sec:antispam}}
\subsection{受信者の承諾を得ずに 大量に送られる電子メール (スパム) に対して、
Mailman ではどんな対策ができますか\label{sec:antispam}}

%en%A technical list's archives may include answers to a range of
%en%different questions.  Often, the people who have posted these answers would
%en%be happy to help someone who doesn't quite understand the answer, and don't
%en%mind giving their address out for that purpose.  But
%en%although it would be wonderful if everyone could contact each other easily,
%en%we also want to make sure that the list and list archives are not abused by 
%en%people who send spam.  

たとえば、技術的な話題のメーリングリストの保存書庫には、
ある分野のさまざまな質問についての答えが保存されるでしょう。
答えを投稿した人たちは、
答えを探しているひとの助けになるようにと思ってそうしたので、
自分のアドレスがまったく別の目的に使われることなど望んではいないでしょう。
みんなが簡単に連絡をとりあえることは素晴らしいことなだけに、
リストやリストの保存書庫が
スパム\footnote{[訳注] なにをスパム (SPAM) 
と呼ぶかは人によって多少違いがあるようですが、
最大公約数的な定義としては、
「受信者の承諾を得ずに、
自動的に大量の宛先に送りつけられる電子メールメッセージ」
ということになると思います。

なお、本文で説明されている対策のうち、投稿の制限などは、
スパムでないいろいろな投稿を禁止するのにも使えます。}
を送る人たちに悪用されないようになっていることを、
はっきりさせておきたいとおもいます。

%en%To make a range of options available to list administrators, Mailman allows
%en%a variety of configurations to help protect email addresses.  
%en%Many of these settings are optional to the list administrator, so your
%en%particular list may be set up in many ways.  List administrators 
%en%must walk a fine line between protecting subscribers and making it difficult
%en%for people to get in touch.  

リスト管理者の取り得る選択肢として、Mailman では電子メールアドレスを
保護するためのさまざまな設定ができるようになっています。
これらの多くの設定はリスト管理者にとって必須のものではありませんが、
リストごとにさまざまな方法で設定ができます。
%???
リスト管理者は、参加者を保護するとともにいろんな人に入手されないように
するため、最良の設定を見付けるべきです。
%???

\begin{itemize}
%en%	\item Subscriber lists
	\item 会員名簿
		\begin{itemize}
%en%			\item The list administrator can choose to have the subscriber list
%en%			public, viewable only to list members, or viewable only to list 
%en%			administrators.
%en%			\item The subscriber list is shown with the addresses obscured to
%en%			make it difficult for spam harvesters to collect your address.
%en%			\item You can choose to have your address hidden from the subscriber
%en%			list.  (See Section~\ref{sec:nolist} for more information.) 
%en%			\item \note{The entire subscriber list is always available to the
%en%			list administrators.}
			\item リスト管理者は、会員名簿を公開するか、
			リスト会員だけが見られるようにするか、
			リスト管理者だけが見ることができるかを選択できます。
			\item 会員名簿のアドレスはぼやかしてあって、
			スパム送信先アドレス収集ソフトウェアが
			アドレスを収集することが難しくなっています。
			\item あなたは
			自分のアドレスを会員名簿で隠すことができます。
			(詳しくは \ref{sec:nolist}~節を見てください。)
			\item \note{リスト管理者は、
			いつでも全会員の名簿を見ることができます。}
		\end{itemize}

%en%	\item List archives
	\item リストの保存書庫
		\begin{itemize}
%en%			\item The list administrator can choose for the archives to be public,
%en%			viewable only to members (private), or completely unavailable.
%en%			\item The HTML archives which are created by Pipermail (the 
%en%			archiving program which comes default with Mailman) contain only
%en%			obscured addresses.  Other archiving programs are available and can
%en%			do different levels of obfuscation to make addresses less readable.
%en%			\item If you wish to be more sure, you can set the mail header
%en%			\mailheader{X-no-archive} and Mailman will not archive your posts.
%en%			\warning{This does not stop other members from quoting your posts,
%en%			possibly even including your email address.}
			\item リスト管理者は、保存書庫を公開するか、
			リスト会員だけが見られるようにする (限定) か、
			まったく作らないかを選択できます。
			\item Pipermail (Mailman に標準で含まれている
			保存書庫作成プログラム) 
			で作成される HTML 保存書庫では、
			アドレスはぼやかしてあります。
%begin general example
			ほかの保存書庫作成プログラムでも、
			アドレスを読み取りにくくするいろいろなレベルの
			ぼやかし機能を持っています。
%end general example
			\item メールに \mailheader{X-no-archive} 
			ヘッダをつけて送ると、Mailman はその投稿を
			保存書庫に入れません。
			\warning{ほかの会員があなたの投稿を
			(場合によってはあなたの電子メールアドレスも含めて)
			引用することを停められるわけではありません。}
		\end{itemize}

%en%	\item Limited posting to the lists
	\item リストへの投稿の制限
		\begin{itemize}
%en%			\item The list administrator can choose who can post to the list.
%en%			Most lists are either moderated (a moderator or administrator
%en%			reviews each posting), set so only subscribers may post to the list,
%en%			or allow anyone to post to the list.
%en%			\item By allowing only subscribers to post to a list, Mailman often 
%en%			blocks all spam and some viruses from being sent through the list.
%en%			As such, this is a fairly common setting used by list administrators.
			\item リスト管理者は、
			誰がリストに投稿できるかを決めることができます。
			たいていのリストは、司会付き
			(司会者や管理者がいちいち投稿をチェックする)
			か、会員のみが投稿できるか、
			だれでも投稿できるか、のいずれかです。
			\item 会員のみが投稿できるようにすると、
			Mailman はほぼすべてのスパムと
			一部のコンピュータウィルスを遮断して、
			リストを通じて送られないようにします。
			そういうわけで、
			この設定はリスト管理者がよく好んで使います。
		\end{itemize}

%en%	\item Anonymous lists
	\item 匿名リスト
		\begin{itemize}
%en%			\item Lists can also be made fully anonymous: all identifying
%en%			information about the sender is stripped from the header before the
%en%			message is sent on.  
%en%			\item This is not typically used for anti-spam measures (it has
%en%			other uses), but it could be used in that way if desired.
			\item リストを完全に匿名にすることもできます。
			つまり、メッセージを送る前に
			ヘッダにある送信者を特定するような情報を全て
			消すようにできます。
			\item これは本来、スパム防止のための機能ではありません
			(ほかの用途があります) が、
			使いたければこのようにも使えます。
		\end{itemize}
\end{itemize}

%en%Of course, many address-obscuring methods can be circumvented by determined 
%en%people, so be aware that the protections used may not be enough.
もちろん、以上のような多くのアドレスぼやかし法は、
気づいた人たちには出し抜かれてしまうので、
保護が完璧なものとは言えないことは知っておいてください。

% ============================================================================
\appendix
% ----------------------------------------------------------------------------
%en%\section{Email commands quick reference\label{a:commands}}
\section{電子メールコマンド クイックリファレンス\label{a:commands}}
\begin{list}{}{}
    \item {confirm <確認文字列>}
               \begin{list}{}{}
	               \item
        実行を確認します. 確認文字列は必須で, 確認要求のメールに
	書かれていなければなりません.
               \end{list}

    \item end
               \begin{list}{}{}
	               \item
        コマンド処理を停止します. メールソフトが自動的に
        署名を追加するのなら, これを使ってください.
               \end{list}

    \item help
		\begin{list}{}{}
			\item
        このヘルプメッセージを要求します.
		\end{list}

    \item info
		\begin{list}{}{}
			\item
        このメーリングリストについての案内を取り出します.
		\end{list}

    \item lists
		\begin{list}{}{}
			\item
        この GNU Mailman サーバの公開メーリングリストの一覧を見る.
		\end{list}

    \item {password [<旧パスワード> <新パスワード>] [address=<アドレス>]}
		\begin{list}{}{}
			\item
        パスワードを取り出したり変更します. 引数がなければ, この
        コマンドで現在のパスワードが取り出せます.
        <旧パスワード>と<新パスワード>の引数があるときには, パス
        ワードを変更します.
        会員登録されたアドレス以外からメールを送っている場合は,
        `address=<アドレス>' (かぎ括弧や引用符は付けないで) で
        登録アドレスを指定してください. この場合, 返信は登録された
        アドレスに宛てられることに注意してください.
		\end{list}

    \item {set ...}
		\begin{list}{}{}
			\item
        会員オプションを設定したり, 確認したりします.

        `set help' (引用符は付けない) で変更可能なオプションの一覧を
        見ることができます.

        `set show' (引用符は付けない) で現在のオプションを見ることが
        できます.
		\end{list}

    \item {subscribe [パスワード] [digest|nodigest] [address=<アドレス>]}
		\begin{list}{}{}
			\item
        このメーリングリストに入会する. パスワードは退会やオプションの
        変更に必要ですが, もし省略した場合には自動的に生成されます.
        パスワードは忘れないように定期的に通知します.

        そのつぎの引数には `nodigest' (通常配送) か `digest' (まとめ読
        み) のいずれか (引用符は付けない!) を書けます. 入会しようとす
        るアドレス以外から申請を出すのであれば, `address=<アドレス>' 
        を指定してください. (このアドレスには <> や " を付けないでく
        ださい!)
		\end{list}

    \item {unsubscribe [パスワード] [address=<アドレス>]}
		\begin{list}{}{}
			\item
        メーリングリストから退会します. もしパスワードを付ける場合,
        登録されたパスワードに一致しないといけません. パス
        ワードを省略した場合には, 退会しようとするアドレスに宛てて
        確認メッセージを発送します. 退会しようとするアドレス以外
        から申請メールを出すのであれば, `address=<アドレス>' を
        指定してください. (このメールアドレスには <> や " を付けな
        いでください!)
		\end{list}

    \item {who [<PASSWORD>] [address=<ADDRESS>]}
		\begin{list}{}{}
			\item
        このメーリングリストの会員名簿を見る. 会員名簿の公開が会員のみに
        限定されている場合は, あなたの会員パスワードを付けなければなりません.
        入会しているアドレス以外送っているのであれば, 
	`address=<アドレス>' で会員アドレスを
        指定してください. (このメールアドレスには <> や " を付けな
        いでください!)
		\end{list}
\end{list}

% ----------------------------------------------------------------------------
%en%\section{Member options quick reference\label{a:options}}
\section{会員オプションコマンド クイックリファレンス\label{a:options}}

\begin{list}{}{}
    \item set help
		\begin{list}{}{}
			\item
        この詳しい説明を取り出す.
		\end{list}

    \item {set show [address=<アドレス>]}
		\begin{list}{}{}
			\item
        現在のオプション設定を見る. あなたが会員登録アドレス以外
        からメールを出している場合には, 登録アドレスを
        `address=<アドレス>' の形式で指定してください. (括弧や引用符を
        メールアドレスに付けないように)
		\end{list}

    \item {set authenticate <パスワード> [address=<アドレス>]}
		\begin{list}{}{}
			\item
        オプションを設定する時には, まずこのコマンドを入れておく必要が
        あります. <パスワード>はあなたの会員パスワードです. 会員として
        登録したアドレス以外からメールを出している場合には, 登録アドレス
        を `address=<アドレス>' の形式で指定してください. (括弧や引用符
        を付けないように)
		\end{list}

    \item set ack on\\
    set ack off
		\begin{list}{}{}
			\item
        `ack' オプションを on にすると, あなたがリストにメールを出す
        度に, 受領確認メッセージを受け取るようになります.
		\end{list}

    \item set digest plain\\
    set digest mime\\
    set digest off
		\begin{list}{}{}
			\item
        `digest' オプションがオフのときは, 投稿されたメッセージをすぐに受け取り
        ます. 何通かあるいは一定期間, 投稿をまとめて読みたいとき, 
        これを平文形式 (RFC 1153 ダイジェスト) で受け取りたい場合には
        `set digest plain' を使ってください. MIME形式のまとめ読みを
        受け取りたい場合には `set digest mime' にしてください. 
		\end{list}

    \item set delivery on\\
    set delivery off
		\begin{list}{}{}
			\item
        配送を on/off します. これは, 退会するのとは違って, 暫くの間
        Mailman がメール配送を止めるようにするだけです. これは, あなたが
        休暇をとるときなどに便利でしょう. 休暇から帰ったら,
        `set delivery on' にするのを忘れないように!
		\end{list}

    \item set myposts on\\
    set myposts off
		\begin{list}{}{}
			\item
        `set myposts off' を使うとあなたがこのリストに投稿したメッセージ
        と同じものは受け取らないようになります. まとめ読みをして
        いる場合には無効です.
		\end{list}

    \item set hide on\\
    set hide off
		\begin{list}{}{}
			\item
        `set hide on' を使うとあなたのメールアドレスが会員名簿には
        出ないようになります.
		\end{list}

    \item set duplicates on\\
    set duplicates off
		\begin{list}{}{}
			\item
        `set duplicates off' にすると, もしあなたのアドレスが明示的に
        To: または Cc: にあったら, Mailman からはあなたにメッセージを送ら
        ようにします. そうすることによってあなたが重複して受け取る
        投稿を減らすことができます.
		\end{list}

    \item set reminders on\\
    set reminders off
		\begin{list}{}{}
			\item
        `set reminders off' にすることで, このリストの毎月のパスワード
        通知を受け取らないようにできます.
		\end{list}
\end{list}

\end{document}
